---
title: "Plant commmunity SSE draft analyses July 2020"
author: "Rita Grunbreg"
date: "6/2/2020"
output: html_document
---

```{r setup,  results='hide', message=FALSE, warning=FALSE}
rm(list = ls())  # clear Rs brain 
# load packages 
library(readr)   # read csv file
library(tidyr)   # tidying data
library(dplyr)   # manipulating df
library(ggplot2) # graphing
library(ggpubr)  # nice package for figures
library(vegan)   # nmds + most community analyses 
library(hillR)   # hill diversity
library(agricolae)# AUDPS
library(emmeans)
library(lmerTest)
library(afex)

cent <- read_csv("C:/Users/grunberg/Documents/GitHub/plant-community-SSE/Data/NMDS_centroids_plant_community_SSE_relative_cover.csv")
cent_pa <- read_csv("C:/Users/grunberg/Documents/Mitchell lab/plant_community_analysis/raw_files/NMDS_centroids_plant_community_SSE_PA_3D.csv")
plant_all <- read_csv("C:/Users/grunberg/Documents/GitHub/plant-community-SSE/Data/NMDS_plant_community_SSE_relative_cover.csv")
plant_all_pa <- read_csv("C:/Users/grunberg/Documents/Mitchell lab/plant_community_analysis/raw_files/NMDS_plant_community_SSE_PA_3D.csv")
plant_groups <- read_csv("C:/Users/grunberg/Dropbox/CURRENT_STUFF/plant_cover_analysis/data/plant_groups.csv")
plant_community <- read_csv("C:/Users/grunberg/Dropbox/CURRENT_STUFF/plant_cover_analysis/data/plant_community_fixed_2Dec2019.csv")
plot_treatment <- read_csv("C:/Users/grunberg/Dropbox/CURRENT_STUFF/plot_treatment.csv")
plotbiomass_2017 <- read_csv("C:/Users/grunberg/Dropbox/CURRENT_STUFF/plant_cover_analysis/data/2017PlotBiomass_SSprayExp.csv")
plotbiomass_2018 <- read_csv("C:/Users/grunberg/Dropbox/CURRENT_STUFF/plant_cover_analysis/data/2018PlotBiomass_SSprayExp.csv")
plotbiomass_2019 <- read_csv("C:/Users/grunberg/Dropbox/CURRENT_STUFF/plant_cover_analysis/data/2019PlotBiomass_SSprayExp.csv")
SSE_prevalence_overall <- read_csv("C:/Users/grunberg/Documents/Mitchell lab/plant_community_analysis/raw_files/SSE_prevalence_overall.csv") #overall prevalence 
SSE_prevalence_spp <- read_csv("C:/Users/grunberg/Documents/Mitchell lab/plant_community_analysis/raw_files/SSE_prevalence_spp.csv")
pcoordO <- read_csv("C:/Users/grunberg/Documents/GitHub/plant-community-SSE/Data/plantsp_coordinates_BC_relative_cover.csv")
#prevalence for each parasite spp. 
plant_height_Widener2020 <- read_csv("C:/Users/grunberg/Documents/GitHub/plant-community-SSE/Data/Plant.height.data_Widener2020.csv")
climate_data_durham <- read_csv("C:/Users/grunberg/Documents/GitHub/plant-community-SSE/Data/climate_data_durham.csv")
```

Description of data files

1. cent [NMDS_centroids_plant_community_SSE.csv] centroids from B-C ordination of plants communities
2. cent_pa [NMDS_centroids_plant_community_SSE_PA_3D.csv] centroids from JAC ordination of plants communities
3. plant_all [NMDS_plant_community_SSE.csv] nmds coordinates based on B-C distances between plants communities 
4. plant_all_pa [NMDS_plant_community_SSE_PA_3D..csv] nmds coordinates based on JAC distances between plants communities 
5. plant_groups [plant_groups.csv] data on plant species: origin, group, family, etc
6. plant_community [plant_community_fixed_2Dec2019.csv] plant community matrix from 2017, 2018, 2019; files has been modified based on Rob's feedback 
7. plotbiomass_2017 [2017PlotBiomass_SSprayExp.csv] plot biomass from SSE 
8. plotbiomass_2018 [2018PlotBiomass_SSprayExp.csv] plot biomass from SSE 
9. plotbiomass_2019 [2019PlotBiomass_SSprayExp.csv] plot biomass from SSE 
10. SSE_prevalence_overall [SSE_prevalence_overall.csv] monthly prevalence data - plot level; cross-species prevalence used
11. SSE_prevalence_spp [SSE_prevalence_plot_level.csv] monthly prevalence data - plot level; prevalence for the three focal pathogens used 


```{r set graphic theme}
rita_theme <-  theme_classic(base_size = 15)+
  theme(legend.title = element_text(size=7, face="bold"),
        legend.text = element_text(size=6.5),
        legend.position=c(0.15,0.18),
        axis.line = element_line(colour = 'black', size = 0.75),
        axis.ticks = element_line(colour = "black", size = 0.75),
        axis.text.x = element_text(size=12,  colour = "black"), 
        axis.text.y = element_text(size=12,  colour = "black"), # bold
        axis.title.y = element_text(size=14, colour = "black")
  )
```

Get the 95% quantile for plant max height from data collection by Brooklynn and Rita in the Widener plots Sept 22 2020

```{r quantile height widner}
plant95quant_widener <- plant_height_Widener2020 %>%
  group_by(Species) %>%
  summarise(Max_height_cm =quantile(Max_height_cm, c( .95))) #%>% #get 95% quantile for max height 
 # filter(Max_height_cm > 30) # remove Poa from dataset, not comfortable with ID 

head(plant95quant_widener)
```

```{r formatting community data}
#add row and column  = post hoc spatial blocks 
plot_treatment$row <- rep(1:16, times=1, each=4) # rep 16 rows, one time for 4 treatments
plot_treatment$column <- rep(seq(1:4), times=16) # rep 1:4, adding column effects 
plot_treatment$Plot <- as.factor(plot_treatment$Plot)
plot_treatment$Treat <- as.factor(plot_treatment$Treat)

#lump paspalum spp. ???; rob not sure how he could discriminate between these two sp., so I am lumping them together 
paspalum <- plant_community %>% select(c(Plot, Year, "Paspalum dilatatum", "Paspalum notatum")) %>% drop_na()
paspalum$Paspalum_sp <- rowSums(paspalum[,3:4])
paspalum <- paspalum %>% select(Plot, Year, Paspalum_sp) 
plant_community <- merge(plant_community, paspalum, by =c("Plot", "Year")) # add paspalum sp.
plant_community <-  subset(plant_community, select = -c(57,59)) # remove paspalum dilatatum and notatum

#merge DFs
plant_community_duex <- merge(plot_treatment, plant_community, by=c('Plot')) 
plant_community_duex$total_cover <- rowSums(plant_community_duex[,c(8:104,106)]) # total cover includes litter 
plant_community_duex$total_cover

# max total cover
max(plant_community_duex$total_cover)
# min total cover 
min(plant_community_duex$total_cover)
hist(plant_community_duex$total_cover, main='Histogram of total plant cover', xlab="Total cover")

plant_community_duex <- subset(plant_community_duex, select = -c(Litter, ...102)) # remove litter not a sp. and random row that got in here 
#plant_community_duex  <- subset(plant_community_duex, select = -c(total_cover)) # remove total_cover

#makes everything relative to total cover; use this for relative abundance data 
relative_cover<-apply(plant_community_duex[,8:105],2, function(x) x/plant_community_duex$total_cover)
total <- rowSums(relative_cover[,1:97]) # checks that this works, so not all plots will add up to 100 because of the litter 
max(total)
min(total)

#new df with relative cover
plant_community_trio <- cbind(plant_community_duex[1:7], relative_cover) 
plant_community_trio <- subset(plant_community_trio, select = -c(total_cover)) # remove total_cover

# add diversity data (hill numbers)
plant_community_diversity <- plant_community_trio %>%
  mutate(sp_rich = renyi(plant_community_trio[8:ncol(plant_community_trio)], scales=c(0), hill = T),
         hill_shannon = renyi(plant_community_trio[8:ncol(plant_community_trio)], scales=c(1), hill = T),
         hill_simpson = renyi(plant_community_trio[8:ncol(plant_community_trio)], scales=c(2), hill = T)
         )
max(plant_community_diversity$sp_rich)
min(plant_community_diversity$sp_rich)

Treat <- c( "C->R->P", "Control", "CR->P" ,"CRP")
Treat_order <- c("1", "4", "2", "3")
trt_ordered <- data.frame(Treat, Treat_order)
trt_ordered <- trt_ordered %>% mutate(Treat_order = as.factor(Treat_order))

```
Using MVabund instead of permanova to evalute differences in community composition due to fungicide treatment

```{r mvabun}
  library(mvabund)
  library(dplyr)
  plant_list <- plant_community_diversity %>%
   select(8:104) %>%
   select_if(colSums(.) != 0) #remove plant sp that don't occur in the data set

  plant_community_diversity <- plant_community_diversity %>% mutate(Year = as.factor(Year))
 plant.data <- mvabund(plant_list)
 is.mvabund(plant.data)
#
# #constrain the permutation within a plot by designating shuffletset; nrow = within the abundance data and control = plot/block
permID <- shuffleSet(n=nrow(plant.data),
                     nset=999,
                     control=how(block=plant_community_diversity$Plot))

mod0 <- manyglm(plant.data ~ plant_community_diversity$Year* plant_community_diversity$Treat,
                family = "negative.binomial", composition = TRUE)
sppcoef <- coef(mod0)
coefplot(mod0)
plot(mod0)
summary(mod0)
set.seed(51)
mod.out <- anova(mod0,
                 bootID=permID,
                 p.uni = 'adjusted',
                 test = 'LR')
mod.out
mod.out.posthoc <- anova(mod0,
                         pairwise.comp = as.factor(plant_community_diversity$Year),
                         bootID=permID, 
                         p.uni = 'adjusted',
                         test = 'LR')
mod.out.posthoc

sp.univariate <- (mod.out$uni.p) %>% as.data.frame()
```

Calc beta diversity with bray curtis matrix in vegan

```{r beta diversity}
dis<-vegdist(plant_list)
dis.mat <- as.matrix(dis) %>% as.data.frame()

dis.clust <- hclust(dis, method="average")

m <- betadiver(plant_list)
d <- betadiver(plant_list, "w") #bray curtis 

hist(dis, xlab='ecological distance', main='Plot')
```

Adding a column that indicates year and log transforming biomass data. Then merge with plant community matrix 

```{r formatting biomass}
biomass_2019 <- plotbiomass_2019 %>%
 # slice(1:64)%>%
  mutate(Year = rep("2019"))  %>% 
  group_by(Plot, Year) %>%
  summarise(total_biomass = (`Plot.biomass(g/m^2)`)) %>% 
  drop_na()
biomass_2019 <- merge(biomass_2019, plot_treatment, by =c('Plot'))

biomass_2018 <- plotbiomass_2018 %>%  ungroup()%>%
  group_by(Plot, Year) %>%
  summarise(total_biomass = sum(`Plot.biomass(g/m^2)`))
biomass_2018 <- merge(biomass_2018, plot_treatment, by =c('Plot'))

biomass_2017 <- plotbiomass_2017 %>%  
  group_by(Plot, Year) %>%
  summarise(total_biomass = sum(`Total.Ovendried.weight(g/m^2)`)) 
biomass_2017 <- merge(biomass_2017, plot_treatment, by =c('Plot'))

biomass <- rbind(biomass_2017, biomass_2018, biomass_2019)
biomass <- biomass %>% 
  mutate(log_biomass = log10(total_biomass),
         Year = as.factor(Year)) %>%
  dplyr::select(Plot, Year, total_biomass, log_biomass)

# merge with community data 
plant_community_biomass <- merge(plant_community_diversity, biomass, by = c("Plot", "Year")) 
```

```{r sorted biomass}
sorted_biomass_2018 <- plotbiomass_2018 %>%  
  group_by(Plot, Year, Biomass.category) %>%
  summarise(total_biomass = (`Plot.biomass(g/m^2)`))
sorted_biomass_2018 <- merge(sorted_biomass_2018, plot_treatment, by =c('Plot'))
sorted_biomass_2018 <- merge(sorted_biomass_2018, trt_ordered, by =c("Treat"))
sorted_biomass_2018 <- sorted_biomass_2018 %>% mutate(Treat_order = as.factor(Treat_order))

sorted_biomass_2018 %>%
  ggplot()+
  geom_boxplot(aes(x= Treat, y = total_biomass, fill=Biomass.category))+ 
  rita_theme+
  labs(x = "",  y = bquote('log'[10]~' plant biomass (g '~m^-2*')'))+
  scale_fill_manual(values=c('#a6611a','#018571','#f5f5f5','#80cdc1','#dfc27d'))+
  theme(legend.position=c(0.13,0.85))

biomass_wide <- sorted_biomass_2018 %>% 
  spread(Biomass.category, total_biomass)%>%
  rename(monocots = 'Non-fescue monocots', dicots = "Non-woody dicots", woody = "Woody dicots")

#MANOVA on all groups
bio.manova <- manova(cbind(Dead, Fescue, monocots, dicots, woody)~Treat, data=biomass_wide)
summary(bio.manova)

library(DescTools)

#ANOVA on fescue
fes.bio <- aov(Fescue ~ Treat, data=biomass_wide)
summary(fes.bio)
EtaSq(fes.bio) # effect size; EtaSq 0.3645689
f.bio_emm <- emmeans(fes.bio , ~ Treat)
pairs(f.bio_emm)
#fescue_biomass <-data.frame(f.bio_emm)

#post hoc groupings for fescue
#C-R-P: c
#Control: a
#CR-P: bc
#CRP: ab

#dead plant biomass
dead.bio <- aov(Dead ~ Treat, data=biomass_wide)
summary(dead.bio)

#non fescue monocots
monocot.bio <- aov(monocots ~ Treat, data=biomass_wide)
summary(monocot.bio)

#non woody dicots
dicot.bio <- aov(dicots ~ Treat, data=biomass_wide)
summary(dicot.bio)

#woody dicots
woody.bio <- aov(woody ~ Treat, data=biomass_wide)
summary(woody.bio)
EtaSq(woody.bio) # effect size; EtaSq 0.1422196 
w.bio_emm <- emmeans(woody.bio , ~ Treat)
pairs(w.bio_emm)

#post hoc groupings for fescue
#C-R-P: ab
#Control: b
#CR-P: b
#CRP: a

dodge <- position_dodge(width = 0.75)

sort_biomass_means <-sorted_biomass_2018 %>%
  group_by(Biomass.category, Treat)%>%
  mutate(mean = mean(total_biomass),
            sd = sd(total_biomass),
            nobs = 16) %>%
  group_by(Biomass.category, Treat)%>%
  mutate(se = sd / sqrt(nobs),
         lower = mean - qt(1 - (0.05 / 2), nobs - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), nobs - 1) * se)%>%
  mutate(Treat_order = as.factor(Treat_order))

#jpeg(file="sorted_biomass_2018.jpeg", width = 140, height = 90, units = 'mm', res = 300)
ggplot(data=sort_biomass_means, aes(x=Treat_order, y = mean, fill=Biomass.category))+
  geom_errorbar(aes(ymin=lower, ymax=upper), data=sort_biomass_means, 
                position=dodge, width=0.1) +
  geom_point(aes(x= Treat_order, y = total_biomass, fill=Biomass.category), pch=21, data = sorted_biomass_2018,
             position=position_jitterdodge(dodge.width=0.75,  jitter.width = 0.05), 
             size=1, alpha=0.35)+ 
  geom_point(aes(x=Treat_order, y =(mean), fill=Biomass.category), size=2.25, pch=21,  position=dodge, data=sort_biomass_means) + 
  rita_theme+
  labs(x = "",  y = bquote('plant biomass (g '~m^-2*')'))+
  scale_fill_manual(values=c('#a6611a','#018571','#f5f5f5','#80cdc1','#dfc27d'),
                    labels=c("litter","fescue", 'non-fescue monocots', 'non-woody dicots', 'woody dicots'))+
  guides(fill=guide_legend("Group",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  scale_x_discrete(labels=c("1" = "never", "2" = "7 months", "3"="9 months", "4"="year-round"))+
  annotate("text", x = 0.85, y = 620, label = "c", size=3) +   #fescue
  annotate("text", x = 1.85, y = 700, label = "bc", size=3) +  #fescue
  annotate("text", x = 2.85, y = 1000, label = "ac", size=3) +  #fescue
  annotate("text", x = 3.85, y = 1050, label = "a", size=3) +  #fescue
  
  annotate("text", x = 1.3, y = 100, label = "ab", size=3) +   #fescue
  annotate("text", x = 2.3, y = 50, label = "b", size=3) +  #fescue
  annotate("text", x = 3.3, y = 200, label = "a", size=3) +  #fescue
  annotate("text", x = 4.3, y = 50, label = "b", size=3) +  #fescue
  theme(legend.position=c(0.15,0.85))
#dev.off()
```

AUDPS calculated across parasite species 

```{r parasite AUDPS cross species}
# designate months as a factor; and put in order 
SSE_prevalence_overall$Month = factor(SSE_prevalence_overall$Month, levels = month.name)
# select target parasite species and months 
SSE_prevalence_overall2 <- SSE_prevalence_overall %>% 
  filter(Month %in% c("May", "June" , "July" , "August", "September", "October", "November"))

# list for loop
year_list <- unique(SSE_prevalence_overall2$Year) 
plot_list <- unique(SSE_prevalence_overall2$Plot)
auc_parasite_all <- data.frame()


for(k in year_list){
  for (i in plot_list){

     #   test <- SSE_prevalence_overall %>% 
      #  arrange(Month)%>%
       # filter(Year == "19") %>% 
      #  filter(Plot == "3") %>% 
      #  mutate(time = seq(1:7)) %>% 
       # ungroup() %>%
      #  dplyr::select(time, Month, prevalence_within_plot)
 
      test <- SSE_prevalence_overall2 %>% 
        arrange(Month)%>%
        filter(Year == k) %>% 
        filter(Plot == i) %>% 
        mutate(time = seq(1,181,by=30 )) %>% 
        ungroup() %>%
        dplyr::select(time, Month, prevalence_within_plot)
      
      AUC <- audps(test$prevalence_within_plot, test$time)
      auc_test <- data.frame(k, i,  AUC)
      auc_parasite_all <- rbind(auc_parasite_all, auc_test)

  }
}

col_head <- c("Year", "Plot",  "AUDPS_parasite")
colnames(auc_parasite_all) <- col_head

auc_parasite_all <- merge(plot_treatment, auc_parasite_all, by ="Plot")
head(auc_parasite_all)
#AUC: the area under the curve of population level (e.g., plot-level) infection over time: from May to Nov. 
#rewording to better integrate files 
auc_parasite_all$Year<-gsub("17", "2017", auc_parasite_all$Year)
auc_parasite_all$Year<-gsub("18", "2018", auc_parasite_all$Year)
auc_parasite_all$Year<-gsub("19", "2019", auc_parasite_all$Year)
#write.csv(auc_parasite_all, "audps_parasite_allspp_SSE171819.csv")

auc_parasite <- auc_parasite_all %>% 
  dplyr::select(Plot, Year, AUDPS_parasite) %>%
  mutate(Plot = as.factor(Plot))
#make the df wide to integrate into other files  
head(auc_parasite_all)
plant_community_disease <- merge(plant_community_biomass, auc_parasite, by = c("Plot", "Year")) 
```

Now df has plant community, diversity, biomass and disease data. Adding information on cover of groups:
Groups include information about plant growth such as forb, grass, woody, legume; exotic or native

```{r add group data}
plant_tidy <- plant_community_disease %>% 
  gather (Species, cover, 8:104) %>% 
  left_join(plant_groups, plant_tidy, by = 'Species')


#add column for total cover of each group: grass, forb, woody, legumes  
plant_growth <- plant_tidy  %>% 
 # group_by(Year, Treat, Plot, Group) %>%
  group_by(Year, Treat, Plot, Growth) %>% 
  summarise_at(c("cover"), sum) %>% 
  ungroup()%>%
  mutate(Year = as.factor(Year),
         Treat = as.factor(Treat))

plant_invasive <- plant_tidy  %>% 
 # group_by(Year, Treat, Plot, Group) %>%
  group_by(Year, Treat, Plot, Origin) %>% 
  summarise_at(c("cover"), sum) %>% 
  ungroup()%>%
  mutate(Year = as.factor(Year),
         Treat = as.factor(Treat)) %>%
  spread(Origin, cover) %>% 
  replace(is.na(.), 0)

#covert to wide df
plant_g_wide <- plant_growth %>% 
  spread(Growth, cover) %>% 
  replace(is.na(.), 0)

#put underscore for fescue 
names(plant_community_disease)[names(plant_community_disease) == "Schedonorus arundinaceus"] <- "Schedonorus_arundinaceus"

#integrate with data 
plant_group_etc_one <- merge(plant_community_disease, plant_g_wide, by =c("Plot", "Year", "Treat"))
plant_group_etc <- merge(plant_group_etc_one, plant_invasive, by =c("Plot", "Year", "Treat"))

```

Calculate the AUDPS for each disease of tall fescue: anthracnose, brown patch, and crown rust

```{r parasite AUDPS for each species}
# designate months as a factor; and put in order 
SSE_prevalence_spp$Month = factor(SSE_prevalence_spp$Month, levels = month.name)
# select target parasite species and months 
SSE_prevalence_spp2 <- SSE_prevalence_spp %>%
  filter(parasite %in% c("Anthracnose","CRust", "Rhiz")) %>%
  filter(Month %in% c("May", "June" , "July" , "August", "September", "October", "November"))



# list for loop
year_list <- unique(SSE_prevalence_spp2$Year) 
plot_list <- unique(SSE_prevalence_spp2$Plot)
parasite_list <- unique(SSE_prevalence_spp2$parasite)
auc_parasite_spp <- data.frame()


for(k in year_list){
  for (i in plot_list){
    for (j in parasite_list){
    
      #  test <- SSE_prevalence_spp %>% 
      #  arrange(Month)%>%
      #  filter(Year == "19") %>% 
      #  filter(Plot == "3") %>% 
      #  filter(parasite == "Anthracnose") %>% 
      #  mutate(time = seq(1:7)) %>% 
      #  ungroup() %>%
      #  select(time, Month, prev_within_plot)
 
      test <- SSE_prevalence_spp2 %>% 
        arrange(Month)%>%
        filter(Year == k) %>% 
        filter(Plot == i) %>% 
        filter(parasite == j) %>% 
        mutate(time = seq(1,181,by=30 )) %>% 
        ungroup() %>%
        dplyr::select(time, Month, prevalence_among_plants)
      
      AUC <- audps(test$prevalence_among_plants, test$time)
      auc_test <- data.frame(k, i, j, AUC)
      auc_parasite_spp <- rbind(auc_parasite_spp, auc_test)
    }
  }
}

col_head <- c("Year", "Plot", "parasite", "AUDPS_parasite")
colnames(auc_parasite_spp) <- col_head

auc_parasite_spp <- merge(plot_treatment, auc_parasite_spp, by ="Plot")
head(auc_parasite_spp)
#AUC: the area under the curve of population level (e.g., plot-level) infection over time: from May to Nov. 
#rewording to better integrate files 
auc_parasite_spp$parasite<-gsub("CRust", "Rust", auc_parasite_spp$parasite)
auc_parasite_spp$Year<-gsub("17", "2017", auc_parasite_spp$Year)
auc_parasite_spp$Year<-gsub("18", "2018", auc_parasite_spp$Year)
auc_parasite_spp$Year<-gsub("19", "2019", auc_parasite_spp$Year)
#write.csv(auc_parasite_spp, "audps_parasite_all_SSE171819.csv")

#make the df wide to integrate into other files  
auc_wide <- auc_parasite_spp %>% 
  spread(parasite, AUDPS_parasite) %>% 
  replace(is.na(.), 0) %>%
  dplyr::select(Plot, Year, Anthracnose, Rhiz, Rust)

#merge with other df
plant_SSE <- merge(plant_group_etc , auc_wide, by = c("Plot", "Year")) 
```

Add treatment ordering for plotting purposed and save output for formatted file as a .csv

```{r formatting}

plant_SSE <- merge(plant_SSE, trt_ordered, by =c("Treat"))
#write.csv(plant_SSE, "plant_SSE.csv")

plant_SSE <- plant_SSE %>% mutate(Plot = as.factor(Plot), 
                                  Year = as.factor(Year), 
                                  Treat = as.factor(Treat), 
                                  row = as.factor(row), 
                                  column = as.factor(column),
                                  Treat_order = as.factor(Treat_order)) 


```


```{r LLR for biomass}
library(boot)
LRR.resamp <- function(x, i) {
  xSub <- x[i, ] #resample x
  LnRR <- 1-(xSub[, 1]/xSub[ ,2])
  return(mean(LnRR))
}

######## 2017 data ##########################
fungicide2017 <- plant_SSE %>% 
  filter(Year =='2017') %>% 
  filter(Treat %in% c("C->R->P")) %>% 
  spread(Treat, total_biomass)%>% select(c("C->R->P"))
  
fungicide2017.control <- plant_SSE %>% 
  filter(Year =='2017') %>% 
  filter(Treat %in% c("Control")) %>% 
  spread(Treat, total_biomass)%>% select(c("Control"))

fungicide2017comp1 <- cbind(fungicide2017.control, fungicide2017)

f2017.1 <- boot(fungicide2017comp1, LRR.resamp, R=999)
plot(f2017.1) #look at distribution of LRRs
out.17.1 <-boot.ci(f2017.1) #calculate CIs for LLR
LLR17.1  <-data.frame(llr=out.17.1$t0, out.17.1$normal, Treat = "1")

######################
fungicide2017.cr_p <- plant_SSE %>% 
  filter(Year =='2017') %>% 
  filter(Treat %in% c("CR->P")) %>% 
  spread(Treat, total_biomass)%>% select(c("CR->P"))

fungicide2017comp2 <- cbind(fungicide2017.cr_p, fungicide2017)

f2017.2 <- boot(fungicide2017comp2, LRR.resamp, R=999)
plot(f2017.2) #look at distribution of LRRs
out.17.2 <-boot.ci(f2017.2) #calculate CIs for LLR
LLR17.2 <-data.frame(llr=out.17.2$t0, out.17.2$normal, Treat = "3")


######################
fungicide2017.crp <- plant_SSE %>% 
  filter(Year =='2017') %>% 
  filter(Treat %in% c("CRP")) %>% 
  spread(Treat, total_biomass)%>% select(c("CRP"))

fungicide2017comp3 <- cbind(fungicide2017.crp, fungicide2017)

f2017.3 <- boot(fungicide2017comp3, LRR.resamp, R=999)
plot(f2017.3) #look at distribution of LRRs
out.17.3 <-boot.ci(f2017.3) #calculate CIs for LLR
LLR17.3 <-data.frame(llr=out.17.3$t0, out.17.3$normal, Treat = "2")

LLR17 <-rbind(LLR17.1, LLR17.2, LLR17.3) %>% mutate(Year = '2017')
########################################################
######## 2018 data ##########################
###########################################
fungicide2018 <- plant_SSE %>% 
  filter(Year =='2018') %>% 
  filter(Treat %in% c("C->R->P")) %>% 
  spread(Treat, total_biomass)%>% select(c("C->R->P"))
  
fungicide2018.control <- plant_SSE %>% 
  filter(Year =='2018') %>% 
  filter(Treat %in% c("Control")) %>% 
  spread(Treat, total_biomass)%>% select(c("Control"))

fungicide2018comp1 <- cbind(fungicide2018.control, fungicide2018)

f2018.1 <- boot(fungicide2018comp1, LRR.resamp, R=999)
plot(f2018.1) #look at distribution of LRRs
out.18.1 <-boot.ci(f2018.1) #calculate CIs for LLR
LLR18.1  <-data.frame(llr=out.18.1$t0, out.18.1$normal, Treat = "1")

######################
fungicide2018.cr_p <- plant_SSE %>% 
  filter(Year =='2018') %>% 
  filter(Treat %in% c("CR->P")) %>% 
  spread(Treat, total_biomass)%>% select(c("CR->P"))

fungicide2018comp2 <- cbind(fungicide2018.cr_p, fungicide2018)

f2018.2 <- boot(fungicide2018comp2, LRR.resamp, R=999)
plot(f2018.2) #look at distribution of LRRs
out.18.2 <-boot.ci(f2018.2) #calculate CIs for LLR
LLR18.2 <-data.frame(llr=out.18.2$t0, out.18.2$normal, Treat = "3")


######################
fungicide2018.crp <- plant_SSE %>% 
  filter(Year =='2018') %>% 
  filter(Treat %in% c("CRP")) %>% 
  spread(Treat, total_biomass)%>% select(c("CRP"))

fungicide2018comp3 <- cbind(fungicide2018.crp, fungicide2018)

f2018.3 <- boot(fungicide2018comp3, LRR.resamp, R=999)
plot(f2018.3) #look at distribution of LRRs
out.18.3 <-boot.ci(f2018.3) #calculate CIs for LLR
LLR18.3 <-data.frame(llr=out.18.3$t0, out.18.3$normal, Treat = "2")

LLR18 <-rbind(LLR18.1, LLR18.2, LLR18.3)%>% mutate(Year = '2018')

######## 2019 data ##########################
fungicide2019 <- plant_SSE %>% 
  filter(Year =='2019') %>% 
  filter(Treat %in% c("C->R->P")) %>% 
  spread(Treat, total_biomass)%>% select(c("C->R->P"))
  
fungicide2019.control <- plant_SSE %>% 
  filter(Year =='2019') %>% 
  filter(Treat %in% c("Control")) %>% 
  spread(Treat, total_biomass)%>% select(c("Control"))

fungicide2019comp1 <- cbind(fungicide2019.control, fungicide2019)

f2019.1 <- boot(fungicide2019comp1, LRR.resamp, R=999)
plot(f2019.1) #look at distribution of LRRs
out.19.1 <-boot.ci(f2019.1) #calculate CIs for LLR
LLR19.1  <-data.frame(llr=out.19.1$t0, out.19.1$normal, Treat = "1")

######################
fungicide2019.cr_p <- plant_SSE %>% 
  filter(Year =='2019') %>% 
  filter(Treat %in% c("CR->P")) %>% 
  spread(Treat, total_biomass)%>% select(c("CR->P"))

fungicide2019comp2 <- cbind(fungicide2019.cr_p, fungicide2019)

f2019.2 <- boot(fungicide2019comp2, LRR.resamp, R=999)
plot(f2019.2) #look at distribution of LRRs
out.19.2 <-boot.ci(f2019.2) #calculate CIs for LLR
LLR19.2 <-data.frame(llr=out.19.2$t0, out.19.2$normal, Treat = "3")


######################
fungicide2019.crp <- plant_SSE %>% 
  filter(Year =='2019') %>% 
  filter(Treat %in% c("CRP")) %>% 
  spread(Treat, total_biomass)%>% select(c("CRP"))

fungicide2019comp3 <- cbind(fungicide2019.crp, fungicide2019)

f2019.3 <- boot(fungicide2019comp3, LRR.resamp, R=999)
plot(f2019.3) #look at distribution of LRRs
out.19.3 <-boot.ci(f2019.3) #calculate CIs for LLR
LLR19.3 <-data.frame(llr=out.19.3$t0, out.19.3$normal, Treat = "2")

LLR19 <-rbind(LLR19.1, LLR19.2, LLR19.3)%>%mutate(Year = '2019')

############################################
############################################
LLR_biomass <-rbind(LLR17, LLR18, LLR19)

LLR_biomass <- LLR_biomass %>% mutate(percent_change = 100*(exp(llr)-1))
############################################ graphic time ###########################################

#jpeg(file="LLR_fungicide_plantbiomass.jpeg", width = 120, height = 90, units = 'mm', res = 300)
LLR_biomass %>% ggplot(aes(x=llr, y = Treat, group=Year))+   
  geom_errorbarh(aes(xmin=V2, xmax=V3),height=0.05)+
  labs(x="biomass response ratio", y = "Fungicide exposure")+
  geom_point(aes(fill=Treat, shape=Year), size=3)+rita_theme+
  scale_fill_manual(values=c('#225ea8','#41b6c4','#a1dab4'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c( "7 months", "9 months", "year-round")) +
  scale_shape_manual(values=c(21,25,22)) + 
  scale_y_discrete(labels=c("3" = "7 months", "2"="9 months", "1"="year-round"))+
  guides(fill=FALSE,
         shape=guide_legend("Year",  keywidth=0.12,
                            keyheight=0.12, 
                            default.unit="inch"))+
  #geom_vline(xintercept = 0, lty=2, color="grey") +
  theme(legend.position=c(0.12,0.87))
#dev.off()
```


Check if relative contribution of each parasite changes to test for change in composition
```{r parasite composition}
plant_parasite <- plant_SSE %>% mutate(relative_anthracnose = Anthracnose/ AUDPS_parasite,
                                       relative_rhiz = Rhiz/ AUDPS_parasite,
                                       relative_rust = Rust/AUDPS_parasite) %>%
  gather(parasite, relative, 124:126) 
  
 df_parasite_comp <- plant_parasite %>%
    group_by(Year, Treat, parasite )%>%
    summarise(mean_relative = mean(relative))

plant_parasite %>%
     group_by(parasite )%>%
     summarise(max_relative = max(relative),
               min_relative = min(relative),
               mean_relative = mean(relative))

#jpeg(file="parasite_spp_contribution.jpeg", width = 220, height = 120, units = 'mm', res = 300)
plant_parasite %>% ggplot(aes(x=Treat_order, y = relative, fill=parasite ))+
  geom_boxplot(aes(x=Treat_order, y = relative, fill=parasite ))+
  facet_wrap(~Year#*parasite, scales='free'
             )+rita_theme+
  guides(fill=guide_legend("",  keywidth=0.20,
                           keyheight=0.20, 
                           default.unit="inch"))+
  scale_fill_manual(values=c('#fc8d62', '#66c2a5','#8da0cb'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("anthracnose", "brown patch", "crown rust")) +
  scale_x_discrete(labels=c("1" = "Never", "2" = "7 months", "3"="9 months", "4"="Year-round"))+
  theme(legend.position = 'top',
        axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1),
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        legend.text = element_text(size=15)
)+
  labs(x="", y ="Relative contribution to cross-species AUDPS")
#dev.off()

```

Check balance of design

```{r checking design}
xtabs(~ Treat + Year, data=plant_SSE)
```
```{r plant species}

plant_relative_diff <- plant_SSE %>%
  gather(species, abundance, 8:104)%>% 
  group_by(species) %>%
  mutate(total_abun = sum(abundance)) %>%
  filter(total_abun >0) %>% ungroup()%>%  
 # filter(abundance > 0)%>%
  group_by(Treat, Year, species) %>%
  mutate(cv = sd(abundance)/mean(abundance))%>%
  ungroup() #%>% filter(!species =="Schedonorus_arundinaceus")

plant_relative_diff %>% 
  ggplot(aes(x=Year, y = cv, fill=Treat_order))+
  geom_boxplot()+rita_theme+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)),
                    labels = c("never", "7 month", "9 month", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)

plant_relative_diff %>% 
  ggplot(aes(x=cv, y = species, fill=Treat_order), pch=21)+
  geom_point()+theme_bw()+
  facet_wrap(~Year)+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)),
                    labels = c("never", "7 month", "9 month", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)

species.mod <- lm((abundance) ~ species *Treat_order * Year, data = plant_relative_diff)
# species_mean<- emmeans(species.mod , ~species *Treat_order * Year) %>% as.data.frame()
# 
# dodge <- position_dodge(width = 0.5)
# 
# species_mean <-species_mean %>% filter(emmean > 0) 
# ggplot(aes(x=(emmean), y = species, fill=Treat_order, group=Treat_order), data= species_mean)+
#   geom_point(aes(x=(emmean), y = species, fill=Treat_order, group=Treat_order), pch=21, position = dodge, size=1.5, data = species_mean)+
#   geom_errorbarh(aes(xmin=(lower.CL), xmax=(upper.CL)), data= species_mean,  position = dodge, width=0.05) +
#   scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
#                     guide=guide_legend(override.aes=list(shape=21)), 
#                     labels = c("never", "7 month", "9 month", "year-round")) +
#   guides(fill=guide_legend("Fungicide",  keywidth=0.12,
#                            keyheight=0.12, override.aes = list(shape=21),
#                            default.unit="inch"), color= FALSE)+
#   theme_bw()+ 
#   facet_wrap(~Year)+
#   labs(x='log mean abundance', y = "")
#%>%
 # group_by(Year, species) %>%
#  summarise(year_round = log(abundance[Treat=="C->R->P"] / abundance[Treat =="Control"]),
 #           july = log(abundance[Treat=="C->R->P"] / abundance[Treat =="CR->P"]),
  #          september = log(abundance[Treat=="C->R->P"] / abundance[Treat =="CRP"])
   #         )%>%
  #replace(is.na(.), 0) %>%
  #gather(treat, LLR, 3:5)

#plant_relative_diff %>% ggplot()+geom_point(aes(x= LLR, y = species, fill=treat), pch=21)+facet_wrap(~Year)+theme_bw()

```

Trying to see if a log respones ratio to fungicide treatment is better for the parasite response to fungicide. Beware long/messy code (-_-)

```{r log response}
library(boot)
LRR.resamp <- function(x, i) {
  xSub <- x[i, ] #resample x
  LnRR <- 1-(xSub[, 1]/xSub[ ,2])
  return(mean(LnRR))
}

######## 2017 data ##########################
fungicide2017 <- plant_SSE %>% 
  filter(Year =='2017') %>% 
  filter(Treat %in% c("C->R->P")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("C->R->P"))
  
fungicide2017.control <- plant_SSE %>% 
  filter(Year =='2017') %>% 
  filter(Treat %in% c("Control")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("Control"))

fungicide2017comp1 <- cbind(fungicide2017.control, fungicide2017)

f2017.1 <- boot(fungicide2017comp1, LRR.resamp, R=999)
plot(f2017.1) #look at distribution of LRRs
out.17.1 <-boot.ci(f2017.1) #calculate CIs for LLR
LLR17.1  <-data.frame(llr=out.17.1$t0, out.17.1$normal, Treat = "1")

######################
fungicide2017.cr_p <- plant_SSE %>% 
  filter(Year =='2017') %>% 
  filter(Treat %in% c("CR->P")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("CR->P"))

fungicide2017comp2 <- cbind(fungicide2017.cr_p, fungicide2017)

f2017.2 <- boot(fungicide2017comp2, LRR.resamp, R=999)
plot(f2017.2) #look at distribution of LRRs
out.17.2 <-boot.ci(f2017.2) #calculate CIs for LLR
LLR17.2 <-data.frame(llr=out.17.2$t0, out.17.2$normal, Treat = "3")


######################
fungicide2017.crp <- plant_SSE %>% 
  filter(Year =='2017') %>% 
  filter(Treat %in% c("CRP")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("CRP"))

fungicide2017comp3 <- cbind(fungicide2017.crp, fungicide2017)

f2017.3 <- boot(fungicide2017comp3, LRR.resamp, R=999)
plot(f2017.3) #look at distribution of LRRs
out.17.3 <-boot.ci(f2017.3) #calculate CIs for LLR
LLR17.3 <-data.frame(llr=out.17.3$t0, out.17.3$normal, Treat = "2")

LLR17 <-rbind(LLR17.1, LLR17.2, LLR17.3) %>% mutate(Year = '2017')
########################################################
######## 2018 data ##########################
###########################################
fungicide2018 <- plant_SSE %>% 
  filter(Year =='2018') %>% 
  filter(Treat %in% c("C->R->P")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("C->R->P"))
  
fungicide2018.control <- plant_SSE %>% 
  filter(Year =='2018') %>% 
  filter(Treat %in% c("Control")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("Control"))

fungicide2018comp1 <- cbind(fungicide2018.control, fungicide2018)

f2018.1 <- boot(fungicide2018comp1, LRR.resamp, R=999)
plot(f2018.1) #look at distribution of LRRs
out.18.1 <-boot.ci(f2018.1) #calculate CIs for LLR
LLR18.1  <-data.frame(llr=out.18.1$t0, out.18.1$normal, Treat = "1")

######################
fungicide2018.cr_p <- plant_SSE %>% 
  filter(Year =='2018') %>% 
  filter(Treat %in% c("CR->P")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("CR->P"))

fungicide2018comp2 <- cbind(fungicide2018.cr_p, fungicide2018)

f2018.2 <- boot(fungicide2018comp2, LRR.resamp, R=999)
plot(f2018.2) #look at distribution of LRRs
out.18.2 <-boot.ci(f2018.2) #calculate CIs for LLR
LLR18.2 <-data.frame(llr=out.18.2$t0, out.18.2$normal, Treat = "3")


######################
fungicide2018.crp <- plant_SSE %>% 
  filter(Year =='2018') %>% 
  filter(Treat %in% c("CRP")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("CRP"))

fungicide2018comp3 <- cbind(fungicide2018.crp, fungicide2018)

f2018.3 <- boot(fungicide2018comp3, LRR.resamp, R=999)
plot(f2018.3) #look at distribution of LRRs
out.18.3 <-boot.ci(f2018.3) #calculate CIs for LLR
LLR18.3 <-data.frame(llr=out.18.3$t0, out.18.3$normal, Treat = "2")

LLR18 <-rbind(LLR18.1, LLR18.2, LLR18.3)%>% mutate(Year = '2018')

######## 2019 data ##########################
fungicide2019 <- plant_SSE %>% 
  filter(Year =='2019') %>% 
  filter(Treat %in% c("C->R->P")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("C->R->P"))
  
fungicide2019.control <- plant_SSE %>% 
  filter(Year =='2019') %>% 
  filter(Treat %in% c("Control")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("Control"))

fungicide2019comp1 <- cbind(fungicide2019.control, fungicide2019)

f2019.1 <- boot(fungicide2019comp1, LRR.resamp, R=999)
plot(f2019.1) #look at distribution of LRRs
out.19.1 <-boot.ci(f2019.1) #calculate CIs for LLR
LLR19.1  <-data.frame(llr=out.19.1$t0, out.19.1$normal, Treat = "1")

######################
fungicide2019.cr_p <- plant_SSE %>% 
  filter(Year =='2019') %>% 
  filter(Treat %in% c("CR->P")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("CR->P"))

fungicide2019comp2 <- cbind(fungicide2019.cr_p, fungicide2019)

f2019.2 <- boot(fungicide2019comp2, LRR.resamp, R=999)
plot(f2019.2) #look at distribution of LRRs
out.19.2 <-boot.ci(f2019.2) #calculate CIs for LLR
LLR19.2 <-data.frame(llr=out.19.2$t0, out.19.2$normal, Treat = "3")


######################
fungicide2019.crp <- plant_SSE %>% 
  filter(Year =='2019') %>% 
  filter(Treat %in% c("CRP")) %>% 
  spread(Treat, AUDPS_parasite)%>% select(c("CRP"))

fungicide2019comp3 <- cbind(fungicide2019.crp, fungicide2019)

f2019.3 <- boot(fungicide2019comp3, LRR.resamp, R=999)
plot(f2019.3) #look at distribution of LRRs
out.19.3 <-boot.ci(f2019.3) #calculate CIs for LLR
LLR19.3 <-data.frame(llr=out.19.3$t0, out.19.3$normal, Treat = "2")

LLR19 <-rbind(LLR19.1, LLR19.2, LLR19.3)%>%mutate(Year = '2019')

############################################
############################################
LLR_experiment <-rbind(LLR17, LLR18, LLR19)

############################################ graphic time ###########################################

#jpeg(file="LLR_fungicide_disease.jpeg", width = 120, height = 90, units = 'mm', res = 300)
LLR_experiment %>% ggplot(aes(x=llr, y = Treat, group=Year))+   
  geom_errorbarh(aes(xmin=V2, xmax=V3),height=0.05)+
  labs(x="disease response ratio", y = "Fungicide exposure")+
  geom_point(aes(fill=Treat, shape=Year), size=3)+rita_theme+
  scale_fill_manual(values=c('#225ea8','#41b6c4','#a1dab4'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c( "7 months", "9 months", "year-round")) +
  scale_shape_manual(values=c(21,25,22)) + 
  scale_y_discrete(labels=c("3" = "7 months", "2"="9 months", "1"="year-round"))+
  guides(fill=FALSE,
         shape=guide_legend("Year",  keywidth=0.12,
                            keyheight=0.12, 
                            default.unit="inch"))+
  #geom_vline(xintercept = 0, lty=2, color="grey") +
  theme(legend.position=c(0.12,0.87))
#dev.off()
```

To determine the effectiveness of the fungicide treatments on pathogen epidemics we used a repeated-measures MANOVA.  The AUDPS of Anthracnose, Rhizoctonia and Rust were the three response vectors, and fungicide treatment, year, and treatment*year interactions were included as fixed effects and plot nested within year was designated as a mixed effect. 

Univariate ANOVAS were used to examine individual dependent variables contribution to main effects 

First look at cross species AUDPS 

```{r disease_anova}
disease_anova <- aov_car((AUDPS_parasite) ~ Year * Treat + Error(Plot/Year), plant_SSE,
                         anova_table = list(correction = "none", es = "pes"))
disease_anova
summary(disease_anova)

cross_disease_emm <- emmeans(disease_anova , ~ Year*Treat)
pwpm(cross_disease_emm, by = "Year") # within year comparisons only 

cross_disease_out <- data.frame(cross_disease_emm)%>%
  mutate_at(c('Year'), ~sub("X", "", .)) # remove random X from column
#cross_disease_out

cross_disease_out<- merge(cross_disease_out, trt_ordered, by =c("Treat"))
```

Visualization of disease and treatment relationship

```{r disease graphic, echo=FALSE}
dodge <- position_dodge(width = 0.75)

#jpeg(file="cross-species_AUDPS.jpeg", width = 90, height = 90, units = 'mm', res = 300)
ggplot(cross_disease_out, aes(x= Year, y = emmean, group=Treat_order))+
  rita_theme+
  geom_point(aes(x=Year, y = AUDPS_parasite, group=Treat_order, fill=Treat_order), 
             pch=21,data =plant_SSE,           
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.20), 
             size=1, alpha=0.35)+
 # geom_errorbar(aes(ymin=mean - std, ymax=mean + std),
  #              position=dodge, width=0.1) +
  geom_errorbar(aes(ymin=lower.CL, ymax=upper.CL), data=cross_disease_out,
                position=dodge, width=0.1) +
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), 
             pch=21, size=2.5, position=dodge)+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 month", "9 month", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  theme(legend.title = element_text(size=7, face="bold"),
        legend.text = element_text(size=6.5))+ 
  annotate("text", x = 0.73, y = 160, label = "h", size=2) + #17 never sprayed
  annotate("text", x = 0.90, y = 140, label = "g", size=2) +  #17 always sprayed
  annotate("text", x = 1.10, y = 130, label = "c", size=2) +  #17 cr->p
  annotate("text", x = 1.25, y = 120, label = "de", size=2) +  #17 crp
  
  annotate("text", x = 1.73, y = 160, label = "h", size=2) + #18 never sprayed
  annotate("text", x = 1.90, y = 140, label = "fg", size=2) +  #18 always sprayed
  annotate("text", x = 2.10, y = 130, label = "cd", size=2) +  #18 cr->p
  annotate("text", x = 2.25, y = 120, label = "de", size=2) +  #18 crp
  
  annotate("text", x = 2.73, y = 130, label = "ef", size=2) + #19 never sprayed
  annotate("text", x = 2.90, y = 70, label = "b", size=2) +  #19 always sprayed
  annotate("text", x = 3.10, y = 45, label = "a", size=2) +  #19 cr->p
  annotate("text", x = 3.25, y = 45, label = "a", size=2)+   #19 crp
  guides(color=FALSE)+  
  labs(x="", y="Cross-disease AUDPS")
#dev.off()
```

```{r parasite_spp, echo=FALSE}
auc_parasite_all <- plant_SSE %>% 
  gather(parasite, AUDPS_parasite, 120:122) %>% 
  group_by(parasite, Treat, Year, Treat_order) %>%
  mutate(mean = mean(AUDPS_parasite), 
         n_obs = 16,
         std = sd(AUDPS_parasite),
         error = qnorm(0.975)*std/sqrt(n_obs)) %>%
  dplyr::select(Year, Treat, parasite, AUDPS_parasite, mean , std, error, Treat_order)

dodge <- position_dodge(width = 0.75)

Trt_names <- list(
  'Anthracnose'="anthracnose",
  'Rhiz'="brown patch",
  'Rust'="crown rust"
  )

Trt_labeller <- function(variable,value){
  return(Trt_names[value])
}


#jpeg(file="AUDPS_SSE_parasite_spp.jpeg", width = 90, height = 270, units = 'mm', res = 300)
ggplot(auc_parasite_all, aes(x= Year, y=AUDPS_parasite, group=Treat_order)) + 
  rita_theme+  
  geom_point(aes(x=Year, y =(AUDPS_parasite), fill=Treat_order), size=1, pch=21,alpha=0.25,
             position=position_jitterdodge(dodge.width=0.75,  jitter.width = 0.25)) + 
  geom_errorbar(aes(ymin=mean - error, ymax=mean + error),position=dodge, width=0.1) +
  geom_point(aes(x=Year, y =(mean), fill=Treat_order), size=2.5, pch=21,  position=dodge) + 
  labs(x="", y="AUDPS")+ #ylim(c(0,4.6))+
  theme(axis.text.x = element_text( angle=90))+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  theme(legend.position=c(0.83,0.18))+
  #guides(fill=FALSE)+
  theme(strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA, size =1),
        strip.text.x = element_text(size = 15))+ # add black square panel around graphic
  facet_wrap(~parasite,  scales = 'free', ncol=1, nrow=3, labeller=Trt_labeller)

#dev.off()
```
Now use manova to asssess whether the three pathogens of tall fescue were affected by the fungicdie treatment 

```{r RM_Manova_disease}
disease_mod_spp <-manova(cbind(Anthracnose,Rust,Rhiz) ~ Treat * Year+ Error(Plot/Year), data= plant_SSE)
summary(disease_mod_spp, 'Wilks')

#dis.mod <- lm(cbind(Anthracnose,Rust,Rhiz) ~ Treat * Year, data= plant_SSE)
#Anova(dis.mod)
#idata <- data.frame(Plot = ordered(plant_SSE$Plot), Year =ordered(plant_SSE$Year))
#Anova(dis.mod, idata = idata, idesign=~Plot*Year)
```

ANOVAs on each pathogen to determine what pathogen is driving the relationship

First Anthracnose 

```{r follow up ANOVA anthracnose}
# ANTHRACNOSE MODEL
anthr.md <- aov((Anthracnose) ~ Treat * Year + Error(Plot/Year), data=plant_SSE)
summary(anthr.md)
EtaSq(anthr.md, type=1, anova=TRUE)

anthr.year.eta <-(summary(anthr.md)[["Error: Plot:Year"]][[1]]["Year" , "F value"]*summary(anthr.md)[["Error: Plot:Year"]][[1]]["Year" , "Df"])/(summary(anthr.md)[["Error: Plot:Year"]][[1]]["Year" , "F value"]*summary(anthr.md)[["Error: Plot:Year"]][[1]]["Year" , "Df"]+summary(anthr.md)[["Error: Plot:Year"]][[1]]["Residuals" , "Df"])
anthr.year.eta

anthr.treat.eta <-(summary(anthr.md)[["Error: Plot"]][[1]]["Treat" , "F value"]*summary(anthr.md)[["Error: Plot"]][[1]]["Treat" , "Df"])/(summary(anthr.md)[["Error: Plot"]][[1]]["Treat" , "F value"]*summary(anthr.md)[["Error: Plot"]][[1]]["Treat" , "Df"]+summary(anthr.md)[["Error: Plot"]][[1]]["Residuals" , "Df"])
anthr.treat.eta
```

Next Rhiz

```{R follow up anova rhiz}
# RHIZ MODEL
rhiz.md <- aov((Rhiz) ~ Treat * Year + Error(Plot/Year), data=plant_SSE)
summary(rhiz.md)
EtaSq(rhiz.md, type=1, anova=TRUE)

rhiz.year.eta <-(summary(rhiz.md)[["Error: Plot:Year"]][[1]]["Year" , "F value"]*summary(rhiz.md)[["Error: Plot:Year"]][[1]]["Year" , "Df"])/(summary(rhiz.md)[["Error: Plot:Year"]][[1]]["Year" , "F value"]*summary(rhiz.md)[["Error: Plot:Year"]][[1]]["Year" , "Df"]+summary(rhiz.md)[["Error: Plot:Year"]][[1]]["Residuals" , "Df"])
rhiz.year.eta

rhiz.treat.eta <-(summary(rhiz.md)[["Error: Plot"]][[1]]["Treat" , "F value"]*summary(rhiz.md)[["Error: Plot"]][[1]]["Treat" , "Df"])/(summary(rhiz.md)[["Error: Plot"]][[1]]["Treat" , "F value"]*summary(rhiz.md)[["Error: Plot"]][[1]]["Treat" , "Df"]+summary(rhiz.md)[["Error: Plot"]][[1]]["Residuals" , "Df"])
rhiz.treat.eta
```

Last Rust 

```{r follow up anova rust}
# RUST MODEL
rust.md <- aov((Rust) ~ Treat * Year + Error(Plot/Year), data=plant_SSE)
summary(rust.md)
EtaSq(rust.md, type=1, anova=TRUE)

rust.year.eta <-(summary(rust.md)[["Error: Plot:Year"]][[1]]["Year" , "F value"]*summary(rust.md)[["Error: Plot:Year"]][[1]]["Year" , "Df"])/(summary(rust.md)[["Error: Plot:Year"]][[1]]["Year" , "F value"]*summary(rust.md)[["Error: Plot:Year"]][[1]]["Year" , "Df"]+summary(rust.md)[["Error: Plot:Year"]][[1]]["Residuals" , "Df"])
rust.year.eta

rust.treat.eta <-(summary(rust.md)[["Error: Plot"]][[1]]["Treat" , "F value"]*summary(rust.md)[["Error: Plot"]][[1]]["Treat" , "Df"])/(summary(rust.md)[["Error: Plot"]][[1]]["Treat" , "F value"]*summary(rust.md)[["Error: Plot"]][[1]]["Treat" , "Df"]+summary(rust.md)[["Error: Plot"]][[1]]["Residuals" , "Df"])
rust.treat.eta
```

We evaluated whether pathogen exclusion, through fungicide application, lowered plant diversity in experimental plots, and how the effects may change across years. Plant diversity was quantified using three metrics: richness, Hill-Shannon diversity (providing a balanced measure of both rare and common species), and Hill-Simpson diversity (emphasizes common species) (Jost 2006). We tested for the effects of fungicide treatment over time on plant biomass and diversity using rm-ANOVAs. All models included fungicide treatment, year, and fungicide treatment*year interactions were as fixed effects and experimental plot nested within year was a mixed effect. Then we evaluated differences among fungicide treatments and years using Tukey’s post hoc tests.


Pt 1a. Does fungicide treatment affect plant richness?

```{r richness}
#Q1.1: Does richness differ between treatment groups 

# set orthogonal contrasts
options(contrasts = c("contr.sum", "contr.poly"))

#RM-ANOVA
sp_aov <- aov_car(log10(sp_rich)~Treat *Year + Error(Plot/Year), data=plant_SSE)
sp_aov
summary(sp_aov)
sp_aov <- aov((sp_rich)~Treat *Year + Error(Plot/Year), data=plant_SSE)

#calculate ETA squ.
rich.year.eta <-(summary(sp_aov)[["Error: Plot:Year"]][[1]]["Year" , "F value"]*summary(sp_aov)[["Error: Plot:Year"]][[1]]["Year" , "Df"])/(summary(sp_aov)[["Error: Plot:Year"]][[1]]["Year" , "F value"]*summary(sp_aov)[["Error: Plot:Year"]][[1]]["Year" , "Df"]+summary(sp_aov)[["Error: Plot:Year"]][[1]]["Residuals" , "Df"])
rich.year.eta

rich.treat.eta <-(summary(sp_aov)[["Error: Plot"]][[1]]["Treat" , "F value"]*summary(sp_aov)[["Error: Plot"]][[1]]["Treat" , "Df"])/(summary(sp_aov)[["Error: Plot"]][[1]]["Treat" , "F value"]*summary(sp_aov)[["Error: Plot"]][[1]]["Treat" , "Df"]+summary(sp_aov)[["Error: Plot"]][[1]]["Residuals" , "Df"])
rich.treat.eta

# post hoc
sp_emm <- emmeans(sp_aov, ~ Treat)
sp_emm
pairs(sp_emm)
plot(emmeans(sp_aov, ~ Treat))

###
#C->R->P Control   CR->P     CRP 
#    "b"     "a"     "a"    "a" 

sp_emm2 <- emmeans(sp_aov, ~ Year)
pairs(sp_emm2)
plot(emmeans(sp_aov, ~ Year))

sp_aov <- aov(log10(sp_rich)~Treat_order *Year + Error(Plot/Year), data=plant_SSE)
sprichout <- emmeans(sp_aov, ~ Year*Treat_order) %>% as.data.frame()
```

In addition to successional changes in plant richness (Year: F = 81.63, p < 0.0001), there were also effects of fungicide treatment on plant richness (Treat: F = 5.23, p = 0.002). Specifically, plots never sprayed with fungicide, that experienced natural levels of disease, had a higher plant richness than plots sprayed with fungicide, that experienced lower levels of disease (Figure below). 

Graphic for plant diversity 

```{r richness graphic, echo=FALSE}
# make nice graphics 
se <- function(x) sqrt(var(x)/length(x))

# first sp richness 
dodge <- position_dodge(width = 0.70)

#jpeg(file="plant_richness_SSE.jpeg",width = 90, height = 90,  units = 'mm',  res = 300) 
rich.graph <-ggplot(data=sprichout, aes(x=Year, y = 10^(emmean), group=Treat_order))+
  rita_theme+
  geom_point(aes(x=Year, y = (sp_rich), group=Treat_order, fill=Treat_order), pch=21, data=plant_SSE, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.1), 
             alpha=0.25)+
  # geom_violin(aes(x=Year, y = sp_rich, group=Treat_order, fill=Treat_order),  data=plant_SSE, alpha=0.35)+
  #geom_errorbar(err_stdev_sp, position=dodge, width=0.1) +
  geom_errorbar(aes(ymin=10^(lower.CL), ymax=10^(upper.CL)),
                position=dodge, width=0.15, data=sprichout) +
  geom_point(aes(x=Year, y = (10^(emmean)), fill=Treat_order), 
             pch=21, size=2.75, position=dodge, data=sprichout)+
  scale_color_manual(values=c('#ffeda0','#a1dab4','#41b6c4','#225ea8')) + 
  labs(x="", y="Richness") +
  theme(legend.title = element_text(size=7, face="bold"),
        legend.text = element_text(size=6.5))+ 
  theme(legend.position=c(0.13,0.90))+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("Never", "7 months", "9 months", 'year-round')) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE) +
 # ylim(c(1,14))+
  annotate("text", x = 1, y = 10.5, label = "B", size=3.5) + #2017
  annotate("text", x = 2, y = 13.5, label = "A", size=3.5) + #2018
  annotate("text", x = 3, y = 10, label = "B", size=3.5) +  #2019
  
  annotate("text", x = 0.73, y = 8.5, label = "a", size=2) + #17 never sprayed
  annotate("text", x = 0.9, y = 8.3, label = "b", size=2) +  #17 always sprayed
  annotate("text", x = 1.10, y = 8.3, label = "b", size=2) +  #17 cr->p
  annotate("text", x = 1.25, y = 8.4, label = "b", size=2) +  #17 crp
  
  annotate("text", x = 1.73, y = 11.2, label = "a", size=2) + #18 never sprayed
  annotate("text", x = 1.9, y = 10.5, label = "b", size=2) +  #18 always sprayed
  annotate("text", x = 2.10, y = 10.5, label = "b", size=2) +  #18 cr->p
  annotate("text", x = 2.25, y = 10.7, label = "b", size=2) +  #18 crp

  annotate("text", x = 2.73, y = 8.1, label = "a", size=2) + #19 never sprayed
  annotate("text", x = 2.9, y = 7.6, label = "b", size=2) +  #19 always sprayed
  annotate("text", x = 3.10, y = 7.6, label = "b", size=2) +  #19 cr->p
  annotate("text", x = 3.25, y = 7.8, label = "b", size=2)
#dev.off()
rich.graph
```

Pt 1. b-c. Does fungicide affect Shannon and Simpson hill diversity 

```{r shannon hill numbers}
#Q1.1: Does richness differ between treatment groups 
shan_aov <- aov_car(hill_shannon~Treat *Year + Error(Plot/Year) , data=plant_SSE)
shan_aov

shan_aov_emm <- emmeans(shan_aov, ~ Treat * Year)
pwpm(shan_aov_emm, by = "Year") # within year comparisons only 

shan_aov <- aov(hill_shannon~Treat_order *Year + Error(Plot/Year) , data=plant_SSE)
shannon_out <- emmeans(shan_aov, ~ Treat_order * Year) %>% as.data.frame()
#plot(emmeans(shan_aov, ~ Treat *Year))

######
```

Year = 2017
        C->R->P Control   CR->P    CRP
C->R->P  [1.58]  0.9716  0.9965 0.9438
Control  0.0849  [1.50]  0.9959 0.7502
CR->P    0.0413 -0.0436  [1.54] 0.8664
CRP     -0.1082 -0.1931 -0.1495 [1.69]

Year = 2018
        C->R->P Control   CR->P    CRP
C->R->P  [3.65]  0.0068  <.0001 <.0001
Control  0.6352  [3.02]  0.1524 0.2030
CR->P    1.0444  0.4092  [2.61] 0.9989
CRP      1.0165  0.3813 -0.0279 [2.64]

Year = 2019
        C->R->P Control   CR->P    CRP
C->R->P  [2.38]  0.0146  0.1639 0.1415
Control  0.5880  [1.79]  0.7720 0.8104
CR->P    0.4023 -0.1857  [1.97] 0.9999
CRP      0.4161 -0.1719  0.0138 [1.96]
```{r shannon graphics, echo=FALSE}
dodge <- position_dodge(width = 0.70)

shannon <-ggplot(data=shannon_out, aes(x=Year, y = emmean, group=Treat_order))+
  geom_point(aes(x=Year, y = hill_shannon,  fill=Treat_order), pch=21, data=plant_SSE, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.10), alpha=0.25)+
  geom_errorbar(aes(ymin=(lower.CL), ymax=(upper.CL)),
                position=dodge, width=0.15, data=shannon_out) +
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), data=shannon_out, pch=21, size=2.75, position=dodge)+
  rita_theme+
  labs(x="", y="Hill Shannon") +
  theme(legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.13,0.85))+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  annotate("text", x = 0.73, y = 2.8, label = "a", size=2) + #17 c-r-p never sprayed
  annotate("text", x = 0.90, y = 2.8, label = "a", size=2) +  #17 cr-p
  annotate("text", x = 1.10, y = 2.8, label = "a", size=2) +  #17 crp
  annotate("text", x = 1.25, y = 2.8, label = "a", size=2) +  #17 control always
  
  annotate("text", x = 1.73, y = 5.3, label = "a", size=2) + #18 never sprayed
  annotate("text", x = 1.90, y = 4.0, label = "b", size=2) +  #18 always sprayed
  annotate("text", x = 2.10, y = 4.0, label = "b", size=2) +  #18 crp
  annotate("text", x = 2.25, y = 4.5, label = "b", size=2) +  #18 control always
  
  annotate("text", x = 2.73, y = 3.5, label = "a", size=2) + #19 never sprayed
  annotate("text", x = 2.90, y = 3, label = "ab", size=2) +  #19 always sprayed
  annotate("text", x = 3.10, y = 3, label = "ab", size=2) +  #19 cr->p
  annotate("text", x = 3.25, y = 3, label = "b", size=2) +  #19 crp
  guides(fill=FALSE)

shannon

```

```{r simpson hill numbers}
################################
simp_aov <- aov_car(hill_simpson~Treat *Year+ Error(Plot/Year) , data=plant_SSE)
simp_aov

simp_aov_emm <- emmeans(simp_aov, ~ Treat * Year)
pwpm(simp_aov_emm, by = "Year") # within year comparisons only 


simp_aov <- aov(hill_simpson~Treat_order *Year+ Error(Plot/Year) , data=plant_SSE)
summary(simp_aov)

#post hoc
simp_emm <- emmeans(simp_aov, ~ Treat_order*Year)
#pairs(simp_emm)

simp_out <- simp_emm %>% as.data.frame()
```
Year = X2017
        C->R->P Control   CR->P    CRP
C->R->P  [1.26]  0.9741  0.9973 0.5984
Control  0.0359  [1.23]  0.9249 0.3466
CR->P   -0.0167 -0.0526  [1.28] 0.7197
CRP     -0.1058 -0.1418 -0.0891 [1.37]

Year = X2018
        C->R->P Control  CR->P    CRP
C->R->P  [2.52]  0.3929 0.0400 0.0138
Control  0.3148  [2.21] 0.6636 0.4161
CR->P    0.5417  0.2269 [1.98] 0.9777
CRP      0.6216  0.3068 0.0799 [1.90]

Year = X2019
         C->R->P  Control    CR->P    CRP
C->R->P   [1.85]   0.0171   0.3959 0.4078
Control  0.41319   [1.44]   0.4590 0.4464
CR->P    0.21391 -0.19927   [1.64] 1.0000
CRP      0.21107 -0.20211 -0.00284 [1.64]
```{r simpson graphic, echo=FALSE}
###############################################
dodge <- position_dodge(width = 0.70)

simpson <-ggplot(data=simp_out, aes(x=Year, y = emmean, group=Treat_order))+
  geom_point(aes(x=Year, y = hill_simpson,  fill=Treat_order), pch=21, data=plant_SSE, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.10), alpha=0.25)+
  geom_errorbar(aes(ymin=(lower.CL), ymax=(upper.CL)),
                position=dodge, width=0.15, data=simp_out) +
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), data=simp_out, pch=21, size=2.75, position=dodge)+
  rita_theme+
 # scale_color_manual(values=c('#ffeda0','#a1dab4','#41b6c4','#225ea8')) + 
  labs(x="", y="Hill Simpson") +
  theme(legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.13,0.85))+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("Control", "July", "Sept", "Continual")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  annotate("text", x = 0.73, y = 2.1, label = "a", size=2) + #17 never sprayed
  annotate("text", x = 0.90, y = 2.1, label = "a", size=2) +  #17 always sprayed
  annotate("text", x = 1.10, y = 2.1, label = "a", size=2) +  #17 cr->p
  annotate("text", x = 1.25, y = 2.1, label = "a", size=2) +  #17 crp
  
  annotate("text", x = 1.73, y = 3.5, label = "a", size=2) + #18 never sprayed
  annotate("text", x = 1.90, y = 3.1, label = "b", size=2) +  #18 always sprayed
  annotate("text", x = 2.10, y = 3.1, label = "b", size=2) +  #18 cr->p
  annotate("text", x = 2.25, y = 3.4, label = "ab", size=2) +  #18 crp
  
  annotate("text", x = 2.73, y = 3.0, label = "a", size=2) + #19 never sprayed
  annotate("text", x = 2.90, y = 2.6, label = "ab", size=2) +  #19 always sprayed
  annotate("text", x = 3.10, y = 2.6, label = "ab", size=2) +  #19 cr->p
  annotate("text", x = 3.25, y = 2.2, label = "b", size=2) #+  #19 crp
  #guides(fill=FALSE)

simpson
```
As charles suggested try paneling by year and not hill index

```{r year focused graphics 2017}
plant_SSE17 <- plant_SSE %>% filter(Year=='2017')
sprichout17 <- sprichout %>% filter(Year=='2017')

richness17 <- ggplot(data=sprichout17, aes(x=Year, y = 10^(emmean), group=Treat_order))+
  rita_theme+
  geom_point(aes(x=Year, y = (sp_rich), group=Treat_order, fill=Treat_order), pch=21, data=plant_SSE17, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.1), 
             alpha=0.25)+
  geom_errorbar(aes(ymin=10^(lower.CL), ymax=10^(upper.CL)),
                position=dodge, width=0.15, data=sprichout17) +
  geom_point(aes(x=Year, y = (10^(emmean)), fill=Treat_order), 
             pch=21, size=2.75, position=dodge, data=sprichout17)+
  scale_color_manual(values=c('#ffeda0','#a1dab4','#41b6c4','#225ea8')) + 
  labs(x="", y="Richness") +
  theme(legend.title = element_text(size=9, face="bold"),
        legend.text = element_text(size=8.5))+ 
  theme(legend.position=c(0.13,0.90))+
#  ylim(c(0,13))+
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE) +
  annotate("text", x = 1, y = 10, label = "B", size=4) + #2017
  annotate("text", x = 0.73, y = 8.5, label = "a", size=3) + #17 never sprayed
  annotate("text", x = 0.9, y = 8.3, label = "b", size=3) +  #17 always sprayed
  annotate("text", x = 1.10, y = 8.3, label = "b", size=3) +  #17 cr->p
  annotate("text", x = 1.25, y = 8.4, label = "b", size=3)  #17 crp
richness17

shannon_out17 <- shannon_out %>% filter(Year=='2017')

shannon17 <-ggplot(data=shannon_out17, aes(x=Year, y = emmean, group=Treat_order))+
  geom_point(aes(x=Year, y = hill_shannon,  fill=Treat_order), pch=21, data=plant_SSE17, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.10), alpha=0.25)+
  geom_errorbar(aes(ymin=(lower.CL), ymax=(upper.CL)),
                position=dodge, width=0.15, data=shannon_out17) +
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), data=shannon_out17, pch=21, size=2.75, position=dodge)+
  rita_theme+
  labs(x="", y="Hill Shannon") +
  theme(legend.title = element_text(size=9, face="bold"),
        legend.text = element_text(size=8.5))+ 
  theme(legend.position=c(0.13,0.85))+
 #   ylim(c(1,5.5))+
  ggtitle(expression(~underline(2017)))+
  theme(plot.title = element_text(hjust = 0.5, size=22))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  annotate("text", x = 0.73, y = 2.5, label = "a", size=3) + #17 never sprayed
  annotate("text", x = 0.90, y = 2.5, label = "a", size=3) +  #17 always sprayed
  annotate("text", x = 1.10, y = 2.5, label = "a", size=3) +  #17 cr->p
  annotate("text", x = 1.25, y = 2.5, label = "a", size=3) +  #17 crp
  guides(fill=FALSE)
shannon17

simp_out17 <- simp_out %>% filter(Year=='2017')

simpson17 <-ggplot(data=simp_out17, aes(x=Year, y = emmean, group=Treat_order))+
  geom_point(aes(x=Year, y = hill_simpson,  fill=Treat_order), pch=21, data=plant_SSE17, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.10), alpha=0.25)+
  geom_errorbar(aes(ymin=(lower.CL), ymax=(upper.CL)),
                position=dodge, width=0.15, data=simp_out17) +
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), data=simp_out17, pch=21, size=2.75, position=dodge)+
  rita_theme+
  labs(x="", y="Hill Simpson") +
  theme(legend.title = element_text(size=9, face="bold"),
        legend.text = element_text(size=8.5))+ 
  theme(legend.position=c(0.13,0.85))+
#  ylim(c(1,4))+
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  annotate("text", x = 0.73, y = 1.75, label = "a", size=3) + #17 never sprayed
  annotate("text", x = 0.90, y = 1.75, label = "a", size=3) +  #17 always sprayed
  annotate("text", x = 1.10, y = 1.75, label = "a", size=3) +  #17 cr->p
  annotate("text", x = 1.25, y = 1.75, label = "a", size=3) +  #17 crp
  guides(fill=FALSE)
simpson17

#jpeg(filename="year_diversitymetrics.jpeg", width=180, height=90, units="mm", bg="white", res=300)
ggarrange(richness17, shannon17, simpson17, ncol=3, common.legend = TRUE)
#dev.off()
```

diversity metrics for 2018 

```{r diverisy metrics 2018}

plant_SSE18 <- plant_SSE %>% filter(Year=='2018')
sprichout18 <- sprichout %>% filter(Year=='2018')

richness18 <- ggplot(data=sprichout18, aes(x=Year, y = 10^(emmean), group=Treat_order))+
  rita_theme+
  geom_point(aes(x=Year, y = (sp_rich), group=Treat_order, fill=Treat_order), pch=21, data=plant_SSE18, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.1), 
             alpha=0.25)+
  geom_errorbar(aes(ymin=10^(lower.CL), ymax=10^(upper.CL)),
                position=dodge, width=0.15, data=sprichout18) +
  geom_point(aes(x=Year, y = (10^(emmean)), fill=Treat_order), 
             pch=21, size=2.75, position=dodge, data=sprichout18)+
  scale_color_manual(values=c('#ffeda0','#a1dab4','#41b6c4','#225ea8')) + 
  labs(x="", y="Richness") +
  theme(legend.title = element_text(size=9, face="bold"),
        legend.text = element_text(size=8.5))+ 
  theme(legend.position=c(0.13,0.90))+
#  ylim(c(0,13))+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE) +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  annotate("text", x = 1, y = 12.5, label = "A", size=4) + #2018
  annotate("text", x = 0.73, y = 11.2, label = "a", size=3) + #18 never sprayed
  annotate("text", x = 0.9, y = 10.5, label = "b", size=3) +  #18 always sprayed
  annotate("text", x = 1.10, y = 10.5, label = "b", size=3) +  #18 cr->p
  annotate("text", x = 1.25, y = 10.7, label = "b", size=3)   #18 crp

richness18

shannon_out18 <- shannon_out %>% filter(Year=='2018')

shannon18 <-ggplot(data=shannon_out18, aes(x=Year, y = emmean, group=Treat_order))+
  geom_point(aes(x=Year, y = hill_shannon,  fill=Treat_order), pch=21, data=plant_SSE18, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.10), alpha=0.25)+
  geom_errorbar(aes(ymin=(lower.CL), ymax=(upper.CL)),
                position=dodge, width=0.15, data=shannon_out18) +
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), data=shannon_out18, pch=21, size=2.75, position=dodge)+
  rita_theme+
  labs(x="", y="Hill Shannon") +
  theme(legend.title = element_text(size=9, face="bold"),
        legend.text = element_text(size=8.5))+ 
  theme(legend.position=c(0.13,0.85))+
 # ylim(c(1,5.5))+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  ggtitle(expression(~underline(2018)))+
  theme(plot.title = element_text(hjust = 0.5, size=22))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  annotate("text", x = 0.73, y = 5.3, label = "a", size=3) + #18 never sprayed
  annotate("text", x = 0.90, y = 4.0, label = "b", size=3) +  #18 always sprayed
  annotate("text", x = 1.10, y = 4.0, label = "b", size=3) +  #18 cr->p
  annotate("text", x = 1.25, y = 4.5, label = "b", size=3) +  #18 crp
  guides(fill=FALSE)

simp_out18 <- simp_out %>% filter(Year=='2018')

simpson18 <-ggplot(data=simp_out18, aes(x=Year, y = emmean, group=Treat_order))+
  geom_point(aes(x=Year, y = hill_simpson,  fill=Treat_order), pch=21, data=plant_SSE18, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.10), alpha=0.25)+
  geom_errorbar(aes(ymin=(lower.CL), ymax=(upper.CL)),
                position=dodge, width=0.15, data=simp_out18) +
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), data=simp_out18, pch=21, size=2.75, position=dodge)+
  rita_theme+
  labs(x="", y="Hill Simpson") +
  theme(legend.title = element_text(size=9, face="bold"),
        legend.text = element_text(size=8.5))+ 
  theme(legend.position=c(0.13,0.85))+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
#  ylim(c(1,4))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  annotate("text", x = 0.73, y = 3.5, label = "a", size=3) + #18 never sprayed
  annotate("text", x = 0.90, y = 3.1, label = "b", size=3) +  #18 always sprayed
  annotate("text", x = 1.10, y = 3.1, label = "b", size=3) +  #18 cr->p
  annotate("text", x = 1.25, y = 3.4, label = "ab", size=3) +  #18 crp
  guides(fill=FALSE)
simpson18

ggarrange(richness18, shannon18, simpson18, ncol=3, common.legend = TRUE, align = 'h')

```

diveristy metrics 2019

```{r diverisy metrics 2019}

plant_SSE19 <- plant_SSE %>% filter(Year=='2019')
sprichout19 <- sprichout %>% filter(Year=='2019')

richness19 <- ggplot(data=sprichout19, aes(x=Year, y = 10^(emmean), group=Treat_order))+
  rita_theme+
  geom_point(aes(x=Year, y = (sp_rich), group=Treat_order, fill=Treat_order), pch=21, data=plant_SSE19, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.1), 
             alpha=0.25)+
  geom_errorbar(aes(ymin=10^(lower.CL), ymax=10^(upper.CL)),
                position=dodge, width=0.15, data=sprichout19) +
  geom_point(aes(x=Year, y = (10^(emmean)), fill=Treat_order), 
             pch=21, size=2.75, position=dodge, data=sprichout19)+
  scale_color_manual(values=c('#ffeda0','#a1dab4','#41b6c4','#225ea8')) + 
  labs(x="", y="Richness") +
  theme(legend.title = element_text(size=9, face="bold"),
        legend.text = element_text(size=8.5))+ 
  theme(legend.position=c(0.13,0.90))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
#  ylim(c(0,13))+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE) +
  annotate("text", x = 1, y = 10, label = "B", size=4) + #2019
  annotate("text", x = 0.73, y = 8.1, label = "a", size=3) + #19 never sprayed
  annotate("text", x = 0.9, y = 7.6, label = "b", size=3) +  #19 always sprayed
  annotate("text", x = 1.10, y = 7.6, label = "b", size=3) +  #19 cr->p
  annotate("text", x = 1.25, y = 7.8, label = "b", size=3)

richness19

shannon_out19 <- shannon_out %>% filter(Year=='2019')

shannon19 <-ggplot(data=shannon_out19, aes(x=Year, y = emmean, group=Treat_order))+
  geom_point(aes(x=Year, y = hill_shannon,  fill=Treat_order), pch=21, data=plant_SSE19, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.10), alpha=0.25)+
  geom_errorbar(aes(ymin=(lower.CL), ymax=(upper.CL)),
                position=dodge, width=0.15, data=shannon_out19) +
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), data=shannon_out19, pch=21, size=2.75, position=dodge)+
  rita_theme+
  labs(x="", y="Hill Shannon") +
  theme(legend.title = element_text(size=9, face="bold"),
        legend.text = element_text(size=8.5))+ 
  theme(legend.position=c(0.13,0.85))+
 # ylim(c(1,5.5))+
  ggtitle(expression(~underline(2019)))+
  theme(plot.title = element_text(hjust = 0.5, size=22))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  annotate("text", x = 0.73, y = 3.5, label = "a", size=3) + #19 never sprayed
  annotate("text", x = 0.90, y = 3, label = "ab", size=3) +  #19 always sprayed
  annotate("text", x = 1.10, y = 3, label = "ab", size=3) +  #19 cr->p
  annotate("text", x = 1.25, y = 3, label = "b", size=3) +  #19 crp
  guides(fill=FALSE)

simp_out19 <- simp_out %>% filter(Year=='2019')

simpson19 <-ggplot(data=simp_out19, aes(x=Year, y = emmean, group=Treat_order))+
  geom_point(aes(x=Year, y = hill_simpson,  fill=Treat_order), pch=21, data=plant_SSE19, 
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.10), alpha=0.25)+
  geom_errorbar(aes(ymin=(lower.CL), ymax=(upper.CL)),
                position=dodge, width=0.15, data=simp_out19) +
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), data=simp_out19, pch=21, size=2.75, position=dodge)+
  rita_theme+
  labs(x="", y="Hill Simpson") +
  theme(legend.title = element_text(size=9, face="bold"),
        legend.text = element_text(size=8.5))+ 
  theme(legend.position=c(0.13,0.85))+
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
 # ylim(c(1,4))+
  annotate("text", x = 0.73, y = 3.0, label = "a", size=3) + #19 never sprayed
  annotate("text", x = 0.90, y = 2.6, label = "ab", size=3) +  #19 always sprayed
  annotate("text", x = 1.10, y = 2.6, label = "ab", size=3) +  #19 cr->p
  annotate("text", x = 1.25, y = 2.2, label = "b", size=3) #+  #19 crp
  guides(fill=FALSE)
simpson19

ggarrange(richness19, shannon19, simpson19, ncol=3, common.legend = TRUE)

```
```{r multipanel diversity graphic}
#jpeg(filename="year_diversitymetrics.jpeg", width=180, height=180, units="mm", bg="white", res=300)
ggarrange(richness17, shannon17, simpson17,
          richness18, shannon18, simpson18,
          richness19, shannon19, simpson19, ncol=3, nrow=3,
          legend="bottom",
          common.legend = TRUE, #labels=c("A", "", "", "B", "", "", "C", "", ""), 
          align="hv")
#dev.off()
```
Pt 2. Does fungicide affect plant community biomass 

```{r biomass}
# RM-ANOVA for biomass within plots
bio_aov <- aov_car(log_biomass~Treat*Year+ Error(Plot/Year), data=plant_SSE)
(bio_aov)

bio_aov <- aov(log_biomass~Treat*Year+ Error(Plot/Year), data=plant_SSE)
summary(bio_aov)

# post hoc
bio_emm <- emmeans(bio_aov, ~ Treat)
pairs(bio_emm)
bio_emm2 <- emmeans(bio_aov, ~ Year)
pairs(bio_emm2)

bio_aov2 <- aov(total_biomass~Treat_order*Year+ Error(Plot/Year), data=plant_SSE)
bio.out <- emmeans(bio_aov2, ~Treat_order*Year) %>%as.data.frame()
```

Total plant biomass increased over time (p < 0.0001) and was also impacted by fungicide treatment (p < 0.0001). Plots more frequently exposed to fungicide (always sprayed and CRP) had the highest biomass and biomass was lowest in plots never sprayed with fungicide. 

```{r biomass graphic , echo=FALSE}
dodge <- position_dodge(width = 0.7)

bio.graph <-ggplot(data=bio.out, aes(x=Year, y = emmean, group=Treat_order))+
  geom_point(aes(x=Year, y = total_biomass, group=Treat_order, fill=Treat_order), pch=21, data=plant_SSE,
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.1), 
             alpha=0.25)+
  geom_errorbar(aes(ymin=(lower.CL), ymax=(upper.CL)),
                position=dodge, width=0.15, data=bio.out) +  
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), 
             pch=21, size=2.75, position=dodge)+
  rita_theme+
  theme(legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.20,0.90))+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  guides(color=FALSE)+
  labs(x = "",  y = bquote('plant biomass (g '~m^-2*')'))+
  annotate("text", x = 1, y = 1700, label = "B", size=4) + #2017
  annotate("text", x = 2, y = 1700, label = "B", size=4) + #2018
  annotate("text", x = 3, y = 2300, label = "A", size=4) +  #2019
  
  annotate("text", x = 0.73, y = 1100, label = "c", size=3) + #17 never sprayed
  annotate("text", x = 0.90, y = 1200, label = "b", size=3) +  #17 always sprayed
  annotate("text", x = 1.10, y = 1300, label = "a", size=3) +  #17 cr->p
  annotate("text", x = 1.25, y = 1300, label = "a", size=3) +  #17 crp
  
  annotate("text", x = 1.73, y = 1100, label = "c", size=3) + #18 never sprayed
  annotate("text", x = 1.90, y = 1200, label = "b", size=3) +  #18 always sprayed
  annotate("text", x = 2.10, y = 1500, label = "a", size=3) +  #18 cr->p
  annotate("text", x = 2.25, y = 1500, label = "a", size=3) +  #18 crp
  
  annotate("text", x = 2.73, y = 1500, label = "c", size=3) + #19 never sprayed
  annotate("text", x = 2.90, y = 1600, label = "b", size=3) +  #19 always sprayed
  annotate("text", x = 3.10, y = 1800, label = "a", size=3) +  #19 cr->p
  annotate("text", x = 3.25, y = 1800, label = "a", size=3)  #19 crp

#jpeg(filename="biomass_trt.jpeg", width=90, height=90, units="mm", bg="white", res=300)
bio.graph
dev.off()
```
We also assessed whether fungicide treatment influenced patterns in plant community composition. Patterns of plant community dissimilarity were visualized using non-metric multidimensional scaling based on Bray-Curtis distances of plant relative cover. A PERMANOVA (function Adonis) was used to test for differences in communities between years and among fungicide treatments (permutations = 999). To determine whether these results were attributed to both patterns in community abundance (i.e., cover) and composition (i.e., presence-absence), we reran this analysis with a presence-absence plant community matrix and a Jaccard index. 

```{r composition_matrix, echo=FALSE }
set.seed(1234567) #make sure to set seed to get the same result, this is a permutation based method 
# create community matrix and envi data matrix 
plant<-plant_SSE[,8:104] # makes new matrix with community data (columns 2-100)
plot<-plant_SSE[,c(1:5,109:110,120:122)]# makes new matrix with envi data (columns 1-3)
plot$Year <- as.factor(plot$Year)
# more formatting
# remove columns 
plant<-plant[, colSums(abs(plant)) !=0] # removes columns with all zeros

# remove rows without plant just in case (residual from using parasite data where you have uninfected hosts )
plant.2<-plant[rowSums(abs(plant))!=0,]  # remove rows with no plant
plot.2<-plot[rowSums(abs(plant))!=0,]  # remove rows with no plant 

plant_pa<-apply(plant.2,2, function(x) {ifelse(x==0,0,1)})  #makes presence-absence matrix

```

We also assessed whether fungicide treatment influenced patterns in plant community composition. Patterns of plant community dissimilarity were visualized using non-metric multidimensional scaling based on Bray-Curtis distances of plant relative cover. A PERMANOVA (function Adonis) was used to test for differences in communities between years and among fungicide treatments (permutations = 999). To determine whether these results were attributed to both patterns in community abundance (i.e., cover) and composition (i.e., presence-absence), we reran this analysis with a presence-absence plant community matrix and a Jaccard index. 

```{r permanova JAC}
set.seed(1234567) #make sure to set seed to get the same result, this is a permutation based method 
#plant_jac.0<-adonis(formula=plant_pa ~ (Treat) + (Year) , data=plot.2, permutations=999, method="jaccard")
#plant_jac.0
#hist(plant_jac.0$f.perms, main="No strata", xlab="F permuted")

#plant_jac<-adonis(formula=plant_pa ~ (Treat) + (Year) , data=plot.2, strata =plot.2$Plot, permutations=999, method="jaccard")
#plant_jac
#hist(plant_jac$f.perms, main="Strata = plot", xlab="F permuted")

plant_jac2<-adonis(formula=plant_pa ~  Treat *(Year) , data=plot.2, strata =plot.2$Plot, permutations=999, method="jaccard")
plant_jac2

#
```

Call:
adonis(formula = plant_pa ~ Treat * (Year), data = plot.2, permutations = 999,      method = "jaccard", strata = plot.2$Plot) 

Blocks:  strata 
Permutation: free
Number of permutations: 999

Terms added sequentially (first to last)

            Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)    
Treat        3     1.204  0.4014  1.7339 0.02350  0.001 ***
Year         2     7.513  3.7564 16.2257 0.14662  0.001 ***
Treat:Year   6     0.852  0.1420  0.6133 0.01663  0.837    
Residuals  180    41.672  0.2315         0.81325           
Total      191    51.241                 1.00000           
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

######################################################################################
```{r permanova BC}
set.seed(1234567) #make sure to set seed to get the same result, this is a permutation based method 
ordO<-metaMDS(plant.2, distance="bray", trymax = 1000, autotransform=FALSE) # not transformed
ordO

fit<-envfit(ordO, plot.2[,6:10],perm=999)#fits vectors
fit # prints coordinates for vectors and test of sig

#plant_bc.0<-adonis(formula=plant.2 ~ Treat + Year, data=plot.2, permutations=999, method="bray")
#plant_bc.0
#hist(plant_bc.0$f.perms, main="No strata", xlab="F permuted")

#plant_bc<-adonis(formula=plant.2 ~ Treat + Year,  strata = plot.2$Plot, data=plot.2, permutations=999, method="bray")
#plant_bc
#hist(plant_bc$f.perms, main="Strata = plot", xlab="F permuted")

plant_bc.2<-adonis(formula=plant.2 ~ Treat * Year,  strata = plot.2$Plot, data=plot.2, permutations=999, method="bray")
plant_bc.2

```
Call:
metaMDS(comm = plant.2, distance = "bray", trymax = 1000, autotransform = FALSE) 

global Multidimensional Scaling using monoMDS

Data:     plant.2 
Distance: bray 

Dimensions: 2 
Stress:     0.1159762 
Stress type 1, weak ties
Two convergent solutions found after 605 tries
Scaling: centring, PC rotation, halfchange scaling 
Species: expanded scores based on ‘plant.2’ 

Conduct pairwise permanvoa for bc model 

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

***VECTORS

                  NMDS1    NMDS2     r2 Pr(>r)  
log_biomass     0.97943  0.20179 0.0305  0.050 *
AUDPS_parasite -0.79624 -0.60498 0.0143  0.263  
Anthracnose    -0.81205 -0.58359 0.0138  0.287  
Rhiz           -0.63938  0.76889 0.0097  0.378  
Rust           -0.91602 -0.40113 0.0056  0.601  
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Permutation: free
Number of permutations: 999


```{r pairwise permanova}
set.seed(1234567) #make sure to set seed to get the same result, this is a permutation based method 

pairwise.adonis <- function(x,factors, sim.method = 'bray', p.adjust.m ='fdr')
  {
  library(vegan)
  co = combn(unique(factors),2)
  pairs = c()
  F.Model =c() 
  R2 = c()
  p.value = c()
  for(elem in 1:ncol(co)){
    ad = adonis(x[factors %in% c(co[1,elem],co[2,elem]),] ~ factors[factors %in% c(co[1,elem],co[2,elem])] , method =sim.method);
    pairs = c(pairs,paste(co[1,elem],'vs',co[2,elem]));
    F.Model =c(F.Model,ad$aov.tab[1,4]);
    R2 = c(R2,ad$aov.tab[1,5]);
    p.value = c(p.value,ad$aov.tab[1,6])
    }
  p.adjusted = p.adjust(p.value,method=p.adjust.m)
  pairw.res = data.frame(pairs,F.Model,R2,p.value,p.adjusted)
  return(pairw.res)
}

plot.2 <- plot.2 %>% mutate(yr = as.numeric(Year))
pair.out <-pairwise.adonis(plant.2, plot.2$Trt.num)
pair.out

pair.out<- as.data.frame(pair.out)

pair.out2 <-pairwise.adonis(plant.2, plot.2$yr)
pair.out2

pair.out2<- as.data.frame(pair.out)
```
Plant community structure differed among fungicide treatments and across years. However, fungicide treatment explained little variation in patterns of plant cover (PERMANOVA on Bray-Curtis distances, Treat: Pseudo-F = 2.38, p =0.001, R2=0.03) and composition (PERMANOVA on Jaccard distances, Treat: Pseudo-F = 1.76, p =0.003, R2=0.02). As expected, year explained more variation in plant cover (PERMANOVA on Bray-Curtis distances, Year: Pseudo-F = 14.17, p =0.001, R2=0.13) and composition (PERMANOVA on Jaccard distances, Year: Pseudo-F = 16.43 p =0.001, R2=0.15).   

Calculate the centroids for the BC NMDS for graphical reasons

```{r NMDS bray curtis}
scrs17 <-scores(ordO, display = "sites", "species")
trt_groups <- (c( 'Treat', 'Year')) 
 
# #extract info for plotting purposes 
 hcoordO<-as.data.frame(scores(ordO, display="sites")) #extracts coordinates for plot
 pcoordO<-as.data.frame(scores(ordO, display="species")) #extracts coordinates for plant vectors
 pcoordO$plant_sp<- rownames(pcoordO, "species")
 pcoordO <- pcoordO %>%   
  separate(col=plant_sp, into = c("Genus", "species"))
 write.csv(pcoordO, 'plantsp_coordinates_BC_relative_cover.csv')
# 
 plant_all <- bind_cols(plot.2, hcoordO)
 plant_all <- merge(plant_all, trt_ordered, by = c("Treat"))
 write.csv(plant_all, "NMDS_plant_community_SSE_relative_cover.csv")
# 
# #should have data for 3 yrs and 4 treatments 
# #calculating centroids 
 cent <-aggregate(scrs17 ~ Treat + Year, data = plant_all, FUN = "mean")
 se <- function(z)sd(z)/sqrt(length(z)) # function to calculate std.err
 ci95 <- function(z) qt(0.025,df=length(z)-1, lower.tail=F)* sd(z)/sqrt(length(z))

cent.95 <- plant_all %>% 
  group_by(Treat, Year) %>% 
  summarise(NMDS1_95= ci95(NMDS1),
            NMDS2_95 = ci95(NMDS2))
cent.SE<- aggregate(scrs17 ~ Treat + Year,data=plant_all,se)
cent <- merge(cent, cent.95, by =c("Treat", "Year"))
# write.csv(cent, "NMDS_centroids_plant_community_SSE_relative_cover.csv")
# 
# topp<-max(cent[,5:6]) #determines maximum and minimum values for the plot axes
# bott<-min(cent[,5:6]) #I draw from both data sets because I make the graph sqaure

plant_all$Year <- as.factor(plant_all$Year)
plant_all$Treat <- as.factor(plant_all$Treat)

plant_all_pa$Year <- as.factor(plant_all_pa$Year)
plant_all_pa$Treat <- as.factor(plant_all_pa$Treat)

cent$Year <- as.factor(cent$Year)
cent_pa$Year <- as.factor(cent_pa$Year)

cent_graph <- merge(cent, trt_ordered, by = c("Treat"))

```

Generate graphic of 1) all NMDS points (all plots) and 2) centroids and 95% CI for those centroids

```{r nmds graphic, echo=FALSE}
ggplot(plant_all, aes(x= NMDS1, y=NMDS2))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
  geom_point(size =2.75, aes(fill=Treat, shape=Year))+
  xlab("NMDS 1 (B-C)") +
  ylab("NMDS 2 (B-C)") +
  #xlim(c( bott, topp)) +
  #ylim(c( bott, topp)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21))) + 
  scale_shape_manual(values=c(21,25,22)) + 
  scale_linetype_manual(values=c(1,3,5)) + 
  theme_pubr() +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position = "top", 
        legend.title = element_blank(),
        legend.box = "horizontal") +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(plot.title = element_text(hjust = 0.5, size=15, face="bold"),
        legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.13,0.85))+
  facet_wrap(~Treat)+
  guides(fill=guide_legend("Treatment",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # add black square panel around graphic


#jpeg(file="plant_community_centroid_SSE_relative.jpeg", width = 90, height = 250, units = 'mm', res = 300)
ggplot(cent_graph, aes(x= NMDS1, y=NMDS2, group=Treat_order))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
  geom_errorbar(aes(ymin=NMDS2 - NMDS2_95,
                    ymax=NMDS2+ NMDS2_95),width=0.05)+
  geom_errorbarh(aes(xmin=NMDS1 -NMDS1_95,
                     xmax=NMDS1 +NMDS1_95),height=0.05)+
  #geom_path(aes(color=Treat), lwd=0.5)+
  geom_point(size =3, data= cent_graph, aes(fill=Treat_order), pch=21)+
  #geom_text(data= pcoordO, aes(x=NMDS1,y=NMDS2, label=Genus), fontface =2, colour = "black" , size=1) + # label year
  xlab("NMDS 1 (B-C)") +
  ylab("NMDS 2 (B-C)") +
  xlim(c( -0.45, 0.9)) +
  ylim(c( -0.45, 0.9)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  scale_color_manual(values=c('#fed976','#a1dab4','#41b6c4','#225ea8'))+
#  scale_shape_manual(values=c(21,25,22)) + 
  theme_pubr() +
  theme(legend.position = "top", legend.title = element_blank(), 
        legend.text = element_text(size=8), legend.box = "horizontal") +
  theme(legend.title = element_text(size=8, face="bold"),
        legend.text = element_text(size=8))+  
  theme(legend.position=c(0.65,0.95))+
  facet_wrap(~Year, ncol=1, nrow = 3)+
  guides(fill=guide_legend("Treatment",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE,
         shape=guide_legend("Year",  keywidth=0.12,
                            keyheight=0.12, 
                            default.unit="inch"))+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) 
#dev.off()
```
Make supp figure with species on NMds diagram

```{r sup figure}

p2017 <- plant_all %>% filter(Year=='2017') 

nmds2017 <- ggplot(p2017, aes(x= NMDS1, y=NMDS2))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
  geom_point(size =2.75, aes(fill=Treat_order), pch=21)+
  xlab("NMDS 1 (B-C)") +
  ylab("NMDS 2 (B-C)") +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  geom_text(data= pcoordO, aes(x=NMDS1,y=NMDS2, label=Genus), fontface =2, colour = "black" , size=2) + # label year
  theme_pubr() +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position = "top", 
        legend.title = element_blank(),
        legend.box = "horizontal") +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(plot.title = element_text(hjust = 0.5, size=15, face="bold"),
        legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.85,0.90))+
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  ggtitle("2017")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # add black square panel around graphic


nmds2017zoom <- ggplot(p2017, aes(x= NMDS1, y=NMDS2))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
  geom_point(size =2.75, aes(fill=Treat_order), pch=21)+
  xlab("NMDS 1 (B-C)") +
  ylab("NMDS 2 (B-C)") +
  xlim(c( -0.30, 0.35)) +
  ylim(c( -0.30, 0.35)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  geom_text(data= pcoordO, aes(x=NMDS1,y=NMDS2, label=Genus), fontface =2, colour = "black" , size=2) + # label year
  theme_pubr() +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position = "top", 
        legend.title = element_blank(),
        legend.box = "horizontal") +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(plot.title = element_text(hjust = 0.5, size=15, face="bold"),
        legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.85,0.90))+
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  ggtitle("2017")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # add black square panel around graphic


p2018 <- plant_all %>% filter(Year=='2018') 

nmds2018 <- ggplot(p2018, aes(x= NMDS1, y=NMDS2))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
  geom_point(size =2.75, aes(fill=Treat_order), pch=21)+
  xlab("NMDS 1 (B-C)") +
  ylab("NMDS 2 (B-C)") +
 # xlim(c( -0.30, 0.35)) +
  #ylim(c( -0.30, 0.35)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  geom_text(data= pcoordO, aes(x=NMDS1,y=NMDS2, label=Genus), fontface =2, colour = "black" , size=2) + # label year
  theme_pubr() +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position = "top", 
        legend.title = element_blank(),
        legend.box = "horizontal") +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(plot.title = element_text(hjust = 0.5, size=15, face="bold"),
        legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.85,0.90))+
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  ggtitle("2018")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # add black square panel around graphic

nmds2018zoom <- ggplot(p2018, aes(x= NMDS1, y=NMDS2))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
  geom_point(size =2.75, aes(fill=Treat_order), pch=21)+
  xlab("NMDS 1 (B-C)") +
  ylab("NMDS 2 (B-C)") +
  xlim(c( -0.30, 0.35)) +
  ylim(c( -0.30, 0.35)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  geom_text(data= pcoordO, aes(x=NMDS1,y=NMDS2, label=Genus), fontface =2, colour = "black" , size=2) + # label year
  theme_pubr() +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position = "top", 
        legend.title = element_blank(),
        legend.box = "horizontal") +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(plot.title = element_text(hjust = 0.5, size=15, face="bold"),
        legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.85,0.90))+
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  ggtitle("2018")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # add black square panel around graphic




p2019 <- plant_all %>% filter(Year=='2019') 

nmds2019 <- ggplot(p2019, aes(x= NMDS1, y=NMDS2))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
  geom_point(size =2.75, aes(fill=Treat_order), pch=21)+
  xlab("NMDS 1 (B-C)") +
  ylab("NMDS 2 (B-C)") +
 # xlim(c( -0.30, 0.35)) +
  #ylim(c( -0.30, 0.35)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  geom_text(data= pcoordO, aes(x=NMDS1,y=NMDS2, label=Genus), fontface =2, colour = "black" , size=2) + # label year
  theme_pubr() +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position = "top", 
        legend.title = element_blank(),
        legend.box = "horizontal") +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(plot.title = element_text(hjust = 0.5, size=15, face="bold"),
        legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.85,0.90))+
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  ggtitle("2019")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # add black square panel around graphic

nmds2019zoom <- ggplot(p2019, aes(x= NMDS1, y=NMDS2))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
  geom_point(size =2.75, aes(fill=Treat_order), pch=21)+
  xlab("NMDS 1 (B-C)") +
  ylab("NMDS 2 (B-C)") +
  xlim(c( -0.30, 0.35)) +
  ylim(c( -0.30, 0.35)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  geom_text(data= pcoordO, aes(x=NMDS1,y=NMDS2, label=Genus), fontface =2, colour = "black" , size=2) + # label year
  theme_pubr() +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position = "top", 
        legend.title = element_blank(),
        legend.box = "horizontal") +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(plot.title = element_text(hjust = 0.5, size=15, face="bold"),
        legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.85,0.90))+
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  ggtitle("2019")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # add black square panel around graphic

#jpeg(file="plant_community_NMDS_species.jpeg", width = 180, height = 250, units = 'mm', res = 300)
ggarrange(nmds2017, nmds2017zoom,
          nmds2018, nmds2018zoom,
          nmds2019, nmds2019zoom,
          ncol=2, nrow = 3, common.legend = TRUE)
#dev.off()
```

Now for Jaccard index NMDS, extrac NMDS coordinates for plotting and centroids. Note that we need 3 axes for this one to reduce stress to an acceptable value. 

```{r NMDS jaccard}
####### now jaccard
# default jaccard doesn't use a PA matrix, still uses abundance, so i convert to PA and then run jaccard 
ordO_p_pa<-metaMDS(plant_pa, distance="jaccard", trymax =1000, k=3,autotransform=FALSE)
ordO_p_pa
#fit<-envfit(ordO_p_pa, plot.2[,6],perm=999)#fits disease vectors (AUDPS) to ordination
#fit # prints coordinates for host vectors and test of sig

scrs_pa <-scores(ordO_p_pa, display = "sites", "species")
trt_groups <- (c( 'Treat', 'Year'))

#extract info for plotting purposes
hcoordO_pa<-as.data.frame(scores(ordO_p_pa, display="sites")) #extracts coordinates for plot
pcoordO_pa<-as.data.frame(scores(ordO_p_pa, display="species")) #extracts coordinates for plant vectors
pcoordO_pa$plant_sp<- rownames(pcoordO_pa, "species")

#add SL mass and FI vectors to parasite vector coords
#NMDS1<-c(fit$vectors$arrows[1,1])
#NMDS2<-c(fit$vectors$arrows[1,2])
#parasite<-data.frame(NMDS1,NMDS2)
#parasite <-parasite %>% mutate(plant_sp = "AUDPS")
#rownames(parasite)<-c("AUDPS")
#pcoordO_pa<-rbind(pcoordO_pa,parasite)

plant_all_pa <- cbind(plot.2, hcoordO_pa)
#write.csv(plant_all_pa, "NMDS_plant_community_SSE_PA_3D.csv")
#write.csv(pcoordO_pa, "NMDS_plant_species_coordinates_SSE_PA.csv")

#should have data for 3 yrs and 4 treatments
#calculating centroids
cent_pa <-aggregate(scrs_pa ~ Treat + Year, data = plant_all_pa, FUN = "mean")
se <- function(z)sd(z)/sqrt(length(z)) # function to calculate std.err
cent.SE.pa<- aggregate(scrs_pa ~ Treat + Year,data=plant_all_pa,se)
cent_pa <- merge(cent_pa, cent.SE.pa, by =c("Treat", "Year"))
#write.csv(cent_pa, "NMDS_centroids_plant_community_SSE_PA_3D.csv")
#topp2<-max(cent_pa[,4:5]) #determines maximum and minimum values for the plot axes
#bott2<-min(cent_pa[,4:5]) #I draw from both data sets because I make the graph sqaure

```
Call:
metaMDS(comm = plant_pa, distance = "jaccard", trymax = 200,      autotransform = FALSE) 

global Multidimensional Scaling using monoMDS

Data:     plant_pa 
Distance: jaccard 

Dimensions: 2 
Stress:     0.2559644 
Stress type 1, weak ties
Two convergent solutions found after 117 tries
Scaling: centring, PC rotation, halfchange scaling 
Species: expanded scores based on ‘plant_pa’ 
########################################################################################################
added 3 axes because of stress : output for ordination used in MS
########################################################################################################
Call:
metaMDS(comm = plant_pa, distance = "jaccard", k = 3, trymax = 1000,      autotransform = FALSE) 

global Multidimensional Scaling using monoMDS

Data:     plant_pa 
Distance: jaccard 

Dimensions: 3 
Stress:     0.1797976 
Stress type 1, weak ties
Two convergent solutions found after 785 tries
Scaling: centring, PC rotation, halfchange scaling 
Species: expanded scores based on ‘plant_pa’ 


```{r nmds graphic jac, echo=FALSE}

plant_all_pa %>% mutate(Year = as.factor(Year))%>%
  ggplot(aes(x= NMDS1, y=NMDS2))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
#  geom_path(aes(color=Treat), lwd=0.5)+
  geom_point(size =2.75, aes(x= NMDS1, y=NMDS2, fill=Treat, shape=Year))+
  xlab("NMDS 1 (JAC)") +
  ylab("NMDS 2 (JAC)") +
  #xlim(c( bott, topp)) +
  #ylim(c( bott, topp)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  scale_color_manual(values=c('#fed976','#a1dab4','#41b6c4','#225ea8'))+
  scale_shape_manual(values=c(21,25,22)) + 
  scale_linetype_manual(values=c(1,3,5)) + 
  rita_theme+
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position = "top", legend.title = element_blank(), 
        legend.text = element_text(size=15), legend.box = "horizontal") +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position=c(0.13,0.85))+
  facet_wrap(~Treat)+
  guides(fill=guide_legend("Treatment",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # add black square panel around graphic

plant_all_pa %>% mutate(Year = as.factor(Year))%>%
ggplot( aes(x= NMDS1, y=NMDS3))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
 # geom_path(aes(color=Plot), lwd=0.5)+
  geom_point(size =2.75, aes(x= NMDS1, y=NMDS2, fill=Treat, shape=Year))+
  xlab("NMDS 1 (JAC)") +
  ylab("NMDS 2 (JAC)") +
  #xlim(c( bott, topp)) +
  #ylim(c( bott, topp)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
 # scale_color_manual(values=c('#fed976','#a1dab4','#41b6c4','#225ea8'))+
  scale_shape_manual(values=c(21,25,22)) + 
  scale_linetype_manual(values=c(1,3,5)) + 
    rita_theme+
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position = "top", legend.title = element_blank(), 
        legend.text = element_text(size=15), legend.box = "horizontal") +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position=c(0.13,0.85))+
  facet_wrap(~Treat)+
  guides(fill=guide_legend("Treatment",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  guides(fill=FALSE, shape=FALSE)+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # 


plant_all_pa %>% mutate(Year = as.factor(Year))%>%
ggplot( aes(x= NMDS2, y=NMDS3))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
 # geom_path(aes(color=Plot), lwd=0.5)+
  geom_point(size =2.75, aes(x= NMDS1, y=NMDS2, fill=Treat, shape=Year))+
  xlab("NMDS 1 (JAC)") +
  ylab("NMDS 2 (JAC)") +
  #xlim(c( bott, topp)) +
  #ylim(c( bott, topp)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
 # scale_color_manual(values=c('#fed976','#a1dab4','#41b6c4','#225ea8'))+
  scale_shape_manual(values=c(21,25,22)) + 
  scale_linetype_manual(values=c(1,3,5)) + 
  rita_theme+
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position = "top", legend.title = element_blank(), 
        legend.text = element_text(size=15), legend.box = "horizontal") +
  guides(colour = guide_legend(override.aes = list(size=70)))+
  theme(legend.position=c(0.13,0.85))+
  facet_wrap(~Treat)+
  guides(fill=guide_legend("Treatment",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  guides(fill=FALSE, shape=FALSE)+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # 
```

```{r jac_nmds_centroid}
cent_pa <- cent_pa %>% mutate(Year = as.factor(Year))

#jpeg(file="plant_community_centroid_SSE.jpeg", width = 90, height = 90, units = 'mm', res = 300)
nmds12 <-cent_pa %>% 
  ggplot(aes(x= NMDS1, y=NMDS2))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
 # geom_path(aes(color=Treat), lwd=0.5)+
  geom_errorbar(aes(ymin=NMDS2 -NMDS2,
                    ymax=NMDS2+NMDS2),width=0.05)+
  geom_errorbarh(aes(xmin=NMDS1 -NMDS1,
                     xmax=NMDS1 +NMDS1),height=0.05)+
  geom_point(size =2.5, data=cent_pa, aes(fill=Treat, shape=Year))+
  xlab("NMDS 1 (JAC)") +
  ylab("NMDS 2 (JAC)") +
   xlim(c(-0.45, 0.5)) +
  ylim(c(-0.45, 0.5)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  scale_color_manual(values=c('#fed976','#a1dab4','#41b6c4','#225ea8'))+
  scale_shape_manual(values=c(21,25,22)) + 
  scale_linetype_manual(values=c(1,3,5)) + 
  rita_theme+
  theme(legend.position = "top", legend.title = element_blank(), 
        legend.text = element_text(size=4.5), legend.box = "horizontal") +
  theme(legend.title = element_text(size=4.5, face="bold"),
        legend.text = element_text(size=3.5))+ 
  theme(legend.position=c(0.80,0.85))+
  guides(fill=guide_legend("Treatment",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE,
         shape=guide_legend("Year",  keywidth=0.12,
                            keyheight=0.12, 
                            default.unit="inch"))+
  facet_wrap(~Year, ncol=1, nrow=3)+
  # geom_segment(data=parasite,aes(x=0,xend=NMDS1,y=0,yend=NMDS2), # vectors for parasite species 
  #             arrow = arrow(length = unit(0.25, "cm")),colour=c("black")) + 
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) # add black square panel around graphic
#dev.off()

nmds13<-cent_pa %>% 
  ggplot(aes(x= NMDS1, y=NMDS3))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
  #geom_path(aes(color=Treat), lwd=0.5)+
  geom_errorbar(aes(ymin=NMDS3 -NMDS3,
                    ymax=NMDS3+NMDS3),width=0.05)+
  geom_errorbarh(aes(xmin=NMDS1 -NMDS1,
                     xmax=NMDS1 +NMDS1),height=0.05)+
  geom_point(size =2.5, data=cent_pa, aes(fill=Treat, shape=Year))+
  xlab("NMDS 1 (JAC)") +
  ylab("NMDS 3 (JAC)") +
   xlim(c(-0.45, 0.5)) +
  ylim(c(-0.45, 0.5)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  scale_color_manual(values=c('#fed976','#a1dab4','#41b6c4','#225ea8'))+
  scale_shape_manual(values=c(21,25,22)) + 
  scale_linetype_manual(values=c(1,3,5)) + 
  rita_theme+
  theme(legend.position = "top", legend.title = element_blank(), 
        legend.text = element_text(size=4.5), legend.box = "horizontal") +
  theme(legend.title = element_text(size=4.5, face="bold"),
        legend.text = element_text(size=3.5))+ 
  theme(legend.position=c(0.80,0.85))+
  guides(fill=guide_legend("Treatment",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE,
         shape=guide_legend("Year",  keywidth=0.12,
                            keyheight=0.12, 
                            default.unit="inch"))+
  facet_wrap(~Year, ncol=1, nrow=3)+
  # geom_segment(data=parasite,aes(x=0,xend=NMDS1,y=0,yend=NMDS2), # vectors for parasite species 
  #             arrow = arrow(length = unit(0.25, "cm")),colour=c("black")) + 
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) 

nmds23<-cent_pa %>% 
  ggplot( aes(x= NMDS2, y=NMDS3))+
  geom_hline(yintercept = 0, lty=2, color="grey") +
  geom_vline(xintercept = 0, lty=2, color="grey") +
 # geom_path(aes(color=Treat), lwd=0.5)+
  geom_errorbar(aes(ymin=NMDS3 -NMDS3,
                    ymax=NMDS3+NMDS3),
                width=0.05)+
  geom_errorbarh(aes(xmin=NMDS2 -NMDS2,
                     xmax=NMDS2 +NMDS2),
                 height=0.05)+
  geom_point(size =2.5, data=cent_pa, aes(fill=Treat, shape=Year))+
  xlab("NMDS 2 (JAC)") +
  ylab("NMDS 3 (JAC)") +
  xlim(c(-0.45, 0.5)) +
  ylim(c(-0.45, 0.5)) +
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("Never", "Always", "CR->P", "CRP")) +
  scale_color_manual(values=c('#fed976','#a1dab4','#41b6c4','#225ea8'))+
  scale_shape_manual(values=c(21,25,22)) + 
  scale_linetype_manual(values=c(1,3,5)) + 
  rita_theme +
  theme(legend.position = "top", legend.title = element_blank(), 
        legend.text = element_text(size=4.5), legend.box = "horizontal") +
  theme(legend.title = element_text(size=4.5, face="bold"),
        legend.text = element_text(size=3.5))+ 
  theme(legend.position=c(0.80,0.85))+
  guides(fill=guide_legend("Treatment",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE,
         shape=guide_legend("Year",  keywidth=0.12,
                            keyheight=0.12, 
                            default.unit="inch"))+
  facet_wrap(~Year, ncol=1, nrow=3)+
  # geom_segment(data=parasite,aes(x=0,xend=NMDS1,y=0,yend=NMDS2), # vectors for species 
  #             arrow = arrow(length = unit(0.25, "cm")),colour=c("black")) + 
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

#jpeg(file="plant_community_centroid_JAC_SSE.jpeg", width = 270, height = 220, units = 'mm', res = 300)
ggarrange(nmds12, nmds13, nmds23, ncol=3, common.legend = TRUE)
#dev.off()
```

Here we are calculating distance from the centroid as a measure of beta diversity 

```{r distance centroid}
cent <- cent %>% dplyr::select(-c(X1))
plant_all <- plant_all %>% dplyr::select(-c(X1))
nmds_all <- merge(cent, plant_all, by = c("Treat", "Year"))
```

```{r dist cent function}
dist.pt <- function(x1, y1, x2, y2) sqrt((x2-x1)^2 + (y2-y1)^2) # finds distance between points 

plot_list <- unique(nmds_all$Plot)
time_list <- unique(nmds_all$Year)

out_centroid <- data.frame()

for (i in plot_list){
  for (j in time_list) {
  plot_id <- i
  year <- j 
  plot_target <- nmds_all %>% 
    filter(Plot == i) %>%
    filter(Year == j)
  
  # plot_target <- nmds_all %>% 
   # filter(Plot == 1) %>%
  #  filter(Year == 2017)
  
  from_center<- dist.pt (as.numeric(plot_target[1,3]),
                         as.numeric(plot_target[1,4]),
                         as.numeric(plot_target[1,15]), 
                         as.numeric(plot_target[1,16] ))
  
  d_cent <- data.frame(i, j, from_center)
  out_centroid <-rbind(out_centroid, d_cent)
  }
}

col_head <- c('Plot', 'Year',  'distance_centroid' )
colnames(out_centroid) <- col_head

drift_cent <- merge(nmds_all, out_centroid, by =c("Plot", "Year"))
```

Produces graphic showing the distance from the centroid over time
Year = X2017
        C->R->P Control   CR->P     CRP
C->R->P [-1.67]  0.9706  0.4277  0.0029
Control  0.0548 [-1.73]  0.2103  0.0007
CR->P   -0.1888 -0.2436 [-1.48]  0.1552
CRP     -0.4521 -0.5069 -0.2633 [-1.22]

Year = X2018
         C->R->P  Control    CR->P      CRP
C->R->P [-0.813]   0.4027   0.9923   0.0003
Control  -0.1750 [-0.638]   0.5720   0.0312
CR->P    -0.0311   0.1438 [-0.782]   0.0007
CRP      -0.4903  -0.3153  -0.4591 [-0.323]

Year = X2019
         C->R->P  Control    CR->P      CRP
C->R->P [-0.747]   0.0816   0.9533   0.0002
Control  -0.2657 [-0.482]   0.0225   0.1843
CR->P     0.0571   0.3228 [-0.804]   <.0001
CRP      -0.4887  -0.2230  -0.5458 [-0.259]

```{r dist_cent_graphic}
dodge <- position_dodge(width = 0.5)

#jpeg(file="distance_centroid_plant_SSE.jpeg", width = 90, height = 90, units = 'mm', res = 300)
drift_cent %>%  mutate(Year = as.factor(Year))%>%
  ggplot(aes(x=Year, y = log10(distance_centroid)))+
  geom_boxplot(aes(x=Year, y = log10(distance_centroid), colour=Treat_order), 
               width=0.5, position = dodge, outlier.colour = NULL)+ 
  geom_boxplot(aes(x=Year, y = log10(distance_centroid), fill=Treat_order),
               width=0.5, position = dodge, outlier.size=-1)+ 
  rita_theme + 
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  theme(legend.position = c(0.15, 0.90))+
  scale_color_manual(values=c('#ffeda0','#a1dab4','#41b6c4','#225ea8'),
                     guide=guide_legend(override.aes=list(shape=21)), 
                     labels = c("never", "7 months", "9 months", "year-round")) +
  labs(x="", y="log distance from centroid")+
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  # 
  annotate("text", x = 0.75, y = -1.0, label = "a", size=2.5) + #17 never sprayed
  annotate("text", x = 0.90, y = -0.85, label = "ab", size=2.5) +  #17 always sprayed
  annotate("text", x = 1.05, y = -0.60, label = "b", size=2.5) +  #17 cr->p
  annotate("text", x = 1.20, y = -0.85, label = "a", size=2.5) +  #17 crp
  #
  annotate("text", x = 1.75, y = 0, label = "a", size=2.5) + #18 never sprayed
  annotate("text", x = 1.90, y = 0, label = "a", size=2.5) +  #18 always sprayed
  annotate("text", x = 2.05, y = 0.25, label = "b", size=2.5) +  #18 cr->p
  annotate("text", x = 2.20, y = 0.10, label = "a", size=2.5) +  #18 crp
  # 
  annotate("text", x = 2.75, y = 0.02, label = "a", size=2.5) + #19 never sprayed
  annotate("text", x = 2.90, y = 0.02, label = "a", size=2.5) +  #19 always sprayed
  annotate("text", x = 3.05, y = 0.28, label = "b", size=2.5) +  #19 cr->p
  annotate("text", x = 3.20, y = 0.25, label = "b", size=2.5)  #19 crp
#dev.off()
```

See if the distance from the centroid varies over time and between treatments.  

```{r RM anova distance centroid}
#cent.mod <- aov(distance_centroid ~ Treat * as.factor(Year), data= drift_cent)
#summary(cent.mod)

drift_cent <- drift_cent %>% 
  mutate(Plot = as.factor(Plot), Year = as.factor(Year),
         log_dist = log10(distance_centroid))
cent.modrm2 <- aov_car(log_dist ~ Treat * Year + Error(Plot/Year), data= drift_cent)
cent.modrm2
summary(cent.modrm2)

dis_aov_emm <- emmeans(cent.modrm2, ~ Treat * Year)
pwpm(dis_aov_emm, by = "Year") # within year comparisons only 
dis_aov_emm <- emmeans(cent.modrm2, ~ Treat * Year)

postcent <- emmeans(cent.modrm2, ~ Year *Treat)
pairs(postcent)

cent.modrm.graph <- aov(log_dist ~ Treat_order * Year, data= drift_cent)
mean.community.var <- emmeans(cent.modrm.graph, ~ Year *Treat_order)%>% as.data.frame()
```

```{r variation final figure}
dodge <- position_dodge(width = 0.7)

variation.graph <-ggplot(data=mean.community.var, aes(x=Year, y = emmean, group=Treat_order))+
  geom_point(aes(x=Year, y = log_dist, group=Treat_order, fill=Treat_order), pch=21, data=drift_cent,
             position=position_jitterdodge(dodge.width=0.70,  jitter.width = 0.1), 
             alpha=0.25)+
  geom_errorbar(aes(ymin=(lower.CL), ymax=(upper.CL)),
                position=dodge, width=0.15, data=mean.community.var) +  
  geom_point(aes(x=Year, y =emmean, fill=Treat_order), 
             pch=21, size=2.75, position=dodge)+
  rita_theme+
  theme(legend.title = element_text(size=8.5, face="bold"),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.20,0.90))+
  scale_fill_manual(values=c('#ffffcc','#a1dab4','#41b6c4','#225ea8'),
                    guide=guide_legend(override.aes=list(shape=21)), 
                    labels = c("never", "7 months", "9 months", "year-round")) +
  guides(fill=guide_legend("Fungicide",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color= FALSE)+
  guides(color=FALSE)+
  labs(x = "",  y = bquote('log'[10]~' distance to centroid'))+
  annotate("text", x = 0.75, y = -1.0, label = "a", size=2.5) + #17 never sprayed
  annotate("text", x = 0.90, y = -0.85, label = "ab", size=2.5) +  #17 always sprayed
  annotate("text", x = 1.07, y = -0.60, label = "b", size=2.5) +  #17 cr->p
  annotate("text", x = 1.25, y = -0.85, label = "a", size=2.5) +  #17 crp
  #
  annotate("text", x = 1.75, y = 0, label = "a", size=2.5) + #18 never sprayed
  annotate("text", x = 1.90, y = 0, label = "a", size=2.5) +  #18 always sprayed
  annotate("text", x = 2.07, y = 0.25, label = "b", size=2.5) +  #18 cr->p
  annotate("text", x = 2.25, y = 0.10, label = "a", size=2.5) +  #18 crp
  # 
  annotate("text", x = 2.75, y = 0.0, label = "a", size=2.5) + #19 never sprayed
  annotate("text", x = 2.90, y = 0.0, label = "a", size=2.5) +  #19 always sprayed
  annotate("text", x = 3.07, y = 0.28, label = "b", size=2.5) +  #19 cr->p
  annotate("text", x = 3.25, y = 0.23, label = "b", size=2.5)  #19 crp

#jpeg(file="FIGURE4_plantcommunityMS.jpeg", width = 90, height = 90, units = 'mm', res = 300)
variation.graph
#dev.off()

```

```{r multivariate heterogenity}
dis<-vegdist(plant.2)
dis.mat <- as.matrix(dis)
meandis <-rowMeans(dis.mat)
plant_SSE$bcdissim <-meandis
plant_SSE$dissim2 <- meanplantdism
plant_SSE %>% ggplot()+geom_boxplot(aes(x=Year, y = bcdissim, fill=Treat))+rita_theme

plant_SSE %>% ggplot()+geom_boxplot(aes(x=Year, y = dissim2, fill=Treat))+rita_theme

dismod <- aov(dissim2 ~ Year * Treat, data= plant_SSE)
summary(dismod)

heatmap(as.matrix(dis))
dis.plot <-meandist(dis, plot.2$Plot)
summary(dis.plot)
plot(dis.plot)
#calculate multivariate dispersion
disp.mod <- betadisper(dis, plot$Treat, type='centroid')
anova(disp.mod)
perm.mod <-permutest(disp.mod, pairwise = TRUE, permutations = 99)
perm.mod
boxplot(disp.mod)

disp.mod2 <- betadisper(dis, plot$Year, type='centroid')
anova(disp.mod2)
perm.mod2 <-permutest(disp.mod2, pairwise = TRUE, permutations = 99)
perm.mod2
boxplot(disp.mod2)
```


